### 2024-12-02 paper/paper.qmd
first draft

---
title: "How do lifestyle and poverty influence BMI across different age groups and genders"
subtitle: "Negative Correlations with Poverty and Physical Activity, Positive Correlations with Age, Sleep Duration, and Gender"
author: 
  - Sakura Hu
thanks: "Code and data are available at: [https://github.com/xycww/BMI](https://github.com/xycww/BMI)."
date: today
date-format: long
abstract: "This paper investigates the relationship between BMI and factors such as lifestyle, poverty, age, and gender, aiming to identify patterns that influence maintaining a healthy BMI. The analysis uses the NHANES dataset from the US National Health and Nutrition Examination Survey and applies a multilinear regression model. The findings suggest weak overall correlations between log(BMI) and the predictors, though some significant patterns are observed: BMI is negatively associated with poverty and physical activity levels and positively associated with age, sleep duration, and being male. These results underscore the complexity of factors influencing BMI and highlight potential areas for targeted public health interventions to promote healthier lifestyles."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(dplyr)
library(knitr)
library(patchwork)
library(arrow)
```

# Introduction

Body mass index (BMI) is a widely used measure for assessing whether an individual's weight is within a healthy range, with significant implications for health outcomes such as heart disease, diabetes, and mortality. Given its importance, understanding the factors that influence BMI, such as socioeconomic and lifestyle variables, has become an essential area of public health research. This paper aims to address the relationship about how variables like poverty, physical activity, age, sleep duration, and gender interact to influence BMI outcomes.

Using data from the US National Health and Nutrition Examination Survey (NHANES), this study models log-transformed BMI as a function of five predictors: poverty level, physical activity frequency (measured in days), age, sleep duration, and gender. A multilinear regression approach was employed to quantify these relationships and identify patterns within the dataset.

The results indicate that while the correlations between BMI and these predictors are generally weak, several significant relationships are observed. Poverty is associated with a 0.01 decrease in log(BMI), suggesting that higher income corresponds to lower BMI levels. Physical activity frequency also demonstrates a negative relationship with BMI; each additional day of physical activity per week is associated with a 0.004 decrease in log(BMI), indicating a modest benefit of regular exercise for maintaining lower BMI. Sleep duration shows a negative relationship, where one additional hour of sleep per night is linked to a 0.01 decrease in log(BMI). In contrast, age is positively associated with BMI, with each additional year corresponding to a 0.001 increase in log(BMI), reflecting the gradual weight gain commonly seen with aging. Lastly, being male is associated with a 0.02 increase in log(BMI) compared to females, suggesting possible physiological or behavioral differences between genders.

These results are essential for informing public health initiatives aimed at addressing weight-related health challenges. By identifying specific socioeconomic and lifestyle factors that influence BMI, this research provides a foundation for developing targeted interventions and strategies to promote healthier weight maintenance.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

The dataset used in this analysis is derived from the US National Health and Nutrition Examination Survey (NHANES), version 2.1.0, published in July 2015. NHANES is a long-running study conducted by the US National Center for Health Statistics (NCHS) that has been gathering health and nutrition data since the early 1960s. Since 1999, approximately 5,000 individuals from various age groups have been interviewed annually in their homes and undergone health examinations at mobile examination centers (MEC). The dataset contains 10,000 observations and 76 variables. The data used here was originally compiled by Michelle Dalrymple from Cashmere High School and Chris Wild from the University of Auckland for educational purposes.

For the current study, the data was cleaned to focus on variables pertinent to the analysis of BMI. Specifically, variables such as BMI, poverty index, physical activity days, sleep hours, gender, and age were retained. After cleaning the missing values in the dataset, 3,573 observations remained. The dataset was prepared, cleaned, and analyzed using R (R Core Team, 2022) with the following libraries: opendatatoronto (Gelfand, 2022) for accessing the data, tidyverse (Wickham et al., 2019), dplyr (Wickham et al., 2023) for data manipulation, and ggplot2 (Wickham, 2016) for visualizations. Additionally, knitr (Xie, 2023a) was used for report generation, and styler (Müller et al., 2024) ensured the R code was properly styled.

A summary table of cleaned data is shown in table 1.

```{r}
#| echo: false
#| label: table-summary
#| tbl-cap: "Summary statistics for variables in the NHANES dataset."

# Load the data
nhanes_data <- read_parquet("/Users/hxw/marriage/data/02-analysis_data/clean_data.parquet")

# Create summary statistics for each variable
summary_table <- nhanes_data %>%
  reframe(
    Variable = c(
      "BMI",
      "log(BMI)",
      "Poverty Index",
      "Physical Activity Days",
      "Age",
      "Sleep Hours"
    ),
    Mean = round(c(
      mean(BMI),
      mean(log(BMI)),
      mean(Poverty),
      mean(PhysActiveDays),
      mean(Age),
      mean(SleepHrsNight)
    ), 3),
    Median = round(c(
      median(BMI),
      median(log(BMI)),
      median(Poverty),
      median(PhysActiveDays),
      median(Age),
      median(SleepHrsNight)
    ), 3),
    Min = round(c(
      min(BMI),
      min(log(BMI)),
      min(Poverty),
      min(PhysActiveDays),
      min(Age),
      min(SleepHrsNight)
    ), 3),
    Max = round(c(
      max(BMI),
      max(log(BMI)),
      max(Poverty),
      max(PhysActiveDays),
      max(Age),
      max(SleepHrsNight)
    ), 3),
    `1st Quantile` = round(
      c(
        quantile(BMI, 0.25),
        quantile(log(BMI), 0.25),
        quantile(Poverty, 0.25),
        quantile(PhysActiveDays, 0.25),
        quantile(Age, 0.25),
        quantile(SleepHrsNight, 0.25)
      ),
      3
    ),
    `3rd Quantile` = round(
      c(
        quantile(BMI, 0.75),
        quantile(log(BMI), 0.75),
        quantile(Poverty, 0.75),
        quantile(PhysActiveDays, 0.75),
        quantile(Age, 0.75),
        quantile(SleepHrsNight, 0.75)
      ),
      3
    )
  )

# Create the summary table using kable
summary_table %>%
  kable(caption = "Summary statistics for variables in the NHANES dataset.")
```

```{r}
#| label: fig-bmi-logbmi
#| fig-cap: "Distributions of BMI and log(BMI) in the NHANES dataset."
#| echo: false
#| fig.width: 8
#| fig.height: 4

# Create histograms with customized text sizes
hist_bmi <- ggplot(nhanes_data, aes(x = BMI)) +
  geom_histogram(binwidth = 1.5,
                 fill = "lightblue",
                 color = "black") +
  labs(title = "BMI Distribution", x = "BMI", y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

hist_log_bmi <- ggplot(nhanes_data, aes(x = log(BMI))) +
  geom_histogram(binwidth = 0.1,
                 fill = "lightblue",
                 color = "black") +
  labs(title = "log(BMI) Distribution", x = "log(BMI)", y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

# Figure 1: BMI and log(BMI)
figure_bmi <- (hist_bmi | hist_log_bmi) +
  plot_annotation(caption = "Figure 1: Distributions of BMI and log(BMI) in the NHANES dataset.",
                  theme = theme(plot.caption = element_text(hjust = 0.5, size = 12)))
figure_bmi

```

```{r}
#| label: fig-predictor-distributions
#| fig-cap: "Distributions of predictor variables in the NHANES dataset, including Poverty, Physical Activity Days, Age, Sleep Hours, and Gender."
#| echo: false
#| fig.width: 8
#| fig.height: 12

hist_poverty <- ggplot(nhanes_data, aes(x = Poverty)) +
  geom_histogram(
    binwidth = 0.8,
    fill = "lightgreen",
    color = "black"
  ) +
  labs(title = "Poverty Index Distribution", x = "Poverty Index", y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

hist_physactive <- ggplot(nhanes_data, aes(x = PhysActiveDays)) +
  geom_histogram(
    binwidth = 1,
    fill = "lightcoral",
    color = "black"
  ) +
  labs(title = "Physical Activity Days Distribution", x = "Physical Activity Days", y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 8)
  )

hist_age <- ggplot(nhanes_data, aes(x = Age)) +
  geom_histogram(
    binwidth = 3.5,
    fill = "lightyellow",
    color = "black"
  ) +
  labs(title = "Age Distribution", x = "Age", y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 8)
  )

hist_sleep <- ggplot(nhanes_data, aes(x = SleepHrsNight)) +
  geom_histogram(binwidth = 1,
                 fill = "lightpink",
                 color = "black") +
  labs(title = "Sleep Hours Distribution", x = "Sleep Hours", y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 8)
  )

hist_gender <- ggplot(nhanes_data, aes(x = Gender)) +
  geom_bar(fill = "lightgray", color = "black") +
  labs(title = "Gender Distribution", x = "Gender", y = "Count") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 8)
  )

# Figure 2: Predictor Variables
figure_predictors <- (hist_poverty | hist_physactive | hist_age) /
  (hist_sleep | hist_gender) +
  plot_annotation(caption = "Figure 2: Distributions of predictor variables in the NHANES dataset, including Poverty, Physical Activity Days, Age, Sleep Hours, and Gender.",
                  theme = theme(plot.caption = element_text(hjust = 0.5, size = 12)))
figure_predictors

```

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

The primary outcome variable in this study is log-transformed BMI, a measure of body mass index adjusted to normalize its distribution. BMI is widely used to assess healthy weight relative to height, and its relevance to health outcomes such as cardiovascular disease and diabetes has been well-established. For this analysis, BMI was log-transformed to address its skewed distribution shown in Figure 1, providing a better fit for statistical modeling.

## Predictor variables
The following predictor variables were examined to assess the potential lifestyle and socio-economic factors influencing BMI:

- `Poverty`: This variable represents the ratio of a family’s income to the federal poverty guidelines, with lower values indicating higher levels of poverty.
- `Physical Activity Days (PhysActiveDays)`: The number of days in a typical week that a participant engages in moderate or vigorous physical activity. This variable is recorded for individuals aged 12 years and older.
- `Sleep Duration (SleepHrsNight)`: The self-reported average number of hours of sleep a participant receives on weekdays or workdays. This variable is recorded for individuals aged 16 years and older.
- `Gender`: The gender of the participant, categorized as male or female.
- `Age`: The participant's age at the time of screening, recorded in years. For participants aged 80 years or older, the age was recorded as 80.

### Distribution of Predictor Variables
The summary statistics presented in Figure 1 and the histograms of predictor variables shown in Figure 3 provide insights into the distribution of these variables:

- `Poverty`: The poverty index ranges from 0 to 5, with a mean of 3.077. The histogram indicates a marked left skew, suggesting that a significant proportion of participants fall into lower income categories.
- `Physical Activity Days (PhysActiveDays)`: The number of days participants engage in physical activity ranges from 2 to 7, with a mean value of 3.7 days per week.
- `Sleep Duration (SleepHrsNight)`:The number of hours participants sleep each night ranges from 2 to 12 hours, with a mean of 6.96 hours. The distribution of this variable approximates a normal curve.
- `Gender`: The gender distribution is nearly balanced, with 1,814 male participants and 1,759 female participants.
- `Age`: The age of participants spans from 16 to 80 years, with a mean age of 43.61 years. The histogram shows a slight right skew, with a concentration of participants aged between 29 and 56 years.

# Model

The goal of our modelling strategy is to use multilinear regression model to investigate the relationship between log(BMI) and poverty, Physical Activity Days, Sleep Duration, gender and age. 
Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $log(BMI)_i$ as the log(BMI). Then $\beta_i$ are the coefficients associated with each predictor variable, which represent the change in $log(BMI)_i$ for a one-unit change in the corresponding predictor, while holding all other predictors constant.

\begin{equation*} 
\log(\text{BMI}_i) = \beta_0 + \beta_1 \cdot \text{Poverty}_i + \beta_2 \cdot \text{PhysActiveDays}_i + \beta_3 \cdot \text{Age}_i + \beta_4 \cdot \text{SleepHrsNight}_i + \beta_5 \cdot \text{Gender}_i + \epsilon_i
\end{equation*}
\begin{equation*}
\epsilon_i \sim \text{Normal}(0, \sigma^2)
\end{equation*}

We ran the model in R [@citeR] using the lm() function for linear regression, with data manipulation performed using the dplyr package and data reading via the arrow package. No specific priors were applied, as this model relies on ordinary least squares (OLS) estimation, which assumes no prior distributions for the coefficients.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

```

```{r}
#| echo: false
#| eval: true

```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}

```

\newpage

# References

### 2024-12-02 scripts/02-download_data.R

@@ -1,26 +1,24 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from IPUMS USA
+# Author: Sakura Hu
+# Date: 01 December 2024
+# Contact: sakura.hu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Download the data from IPUMS USA
+# Any other information needed? Data was downloaded on November 20, 2024
+
 
 
 #### Workspace setup ####
-library(opendatatoronto)
-library(tidyverse)
-# [...UPDATE THIS...]
+library(NHANES)
+library(dplyr)
+library(ggplot2)
+library(arrow)
 
-#### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
-
+# Load the main NHANES dataset
+data("NHANES")
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+write_parquet(NHANES, "data/01-raw_data/raw_data.parquet")
 
          

### 2024-12-02 scripts/03-clean_data.R

@@ -1,44 +1,34 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw marriage data recorded by IPUMS USA
+# Author: Sakura Hu
+# Date: 01 December 2024
+# Contact: sakura.hu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# - The raw marriage data must be downloaded and saved as a parquet to data/raw_data.
+# - The `tidyverse` packages must be installed and loaded.
+# - 02-download_data.R must have been run.
+# Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
+library(arrow)
 
-#### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+# Load raw data
+raw_data <- read_parquet("data/01-raw_data/raw_data.parquet")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
[…]

### 2024-12-02 scripts/06-model_data.R

@@ -1,37 +1,29 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models the marriage rate
+# Author: Sakura Hu
+# Date: 01 December 2024
+# Contact: sakura.hu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run 01-download_data.R and 03-clean_data.R
+# Any other information needed? None
 
 
 #### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
+library(dplyr)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+model_data <- read_parquet("data/02-analysis_data/clean_data.parquet")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Convert Gender to a factor
+model_data$Gender <- as.factor(model_data$Gender)
 
+# Fit a linear model
+lm_model <- lm(log(BMI) ~ Poverty + PhysActiveDays + Age + SleepHrsNight + Gender,
+               data = model_data)
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+# Summary of the model (optional to display)
+summary(lm_model)
 
-
+# Save the model as an RDS file
+saveRDS(lm_model, "models/lm_model.rds")

### 2024-12-03 paper/paper.qmd
second draft. Left with: readme, bib, paper, sketch

@@
 library(arrow)
+library(broom)
 ```
@@
 ### Model justification
+We use a multiple linear regression model to estimate the relationship between body mass index (BMI) and various predictors, including poverty index, physical activity days, age, sleep hours, and gender.
+The model is designed to predict log-transformed BMI, as this transformation helps normalize the distribution of BMI and address skewness.
+This approach allows us to explore how these lifestyle and socio-economic factors influence BMI across the sample, using high-quality survey data from the NHANES dataset.
+We employ predictors like poverty, physical activity, age, sleep hours, and gender to account for key factors that are known to influence BMI, based on existing research.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We use linear regression because it is appropriate for modeling the relationship between a continuous outcome variable (log(BMI)) and predictors physical activity, sleep hours, age, poverty, and gender.
+This method is straightforward to interpret, and the results could quantify the effect of predictors on BMI, making it a suitable choice for analyzing how these factors relate to BMI.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+We chose to log-transform the BMI variable due to its right-skewed distribution.
+Log-transforming BMI allows us to better meet the assumptions of linear regression by stabilizing variance and making the relationship between BMI and predictors more linear.
+This is particularly important for ensuring that the model’s estimates are valid and interpretable.
+
+We included the variable 'Poverty' to account for socio-economic status, as previous research has suggested that lower-income individuals tend to have higher BMI levels (Webber et al., 2023).
+'PhysActiveDays' was included to capture the effect of physical activity on BMI, as increased physical activity is typically associated with a lower BMI(Webber et al., 2023).
+Age was included as a predictor to account for the natural changes in BMI that occur as individuals age.
+Sleep hours were added because there is evidence that insufficient sleep can contribute to weight gain (Ekstedt et al., 2013).
+Gender was included as a predictor due to well-established gender differences in BMI, with males typically having lower BMI than females (Longo-Silva et al., 2023).
+
+We used the default settings in lm() from the stats package, which assumes normally distributed errors and does not apply any specific prior distributions, as this method does not require priors in the same way that Bayesian methods do.
+This approach provides a reliable way to assess the linear relationship between the predictors and BMI.
+However, we acknowledge that other methods, such as Bayesian regression or generalized linear models, could be used for more complex modeling, but this approach was selected for its simplicity and interpretability given the goals of the analysis.
+
+Initially, we considered including interaction terms between predictors (such as between poverty and physical activity).
+However, when these interaction terms were added, the R-squared value decreased, indicating a reduced fit to the data.
+Additionally, the residual plot showed a noticeable concentration in the residuals, suggesting potential model misspecification or overfitting.
+As a result, we decided to exclude interaction terms to maintain a more interpretable and well-fitted model.
+Future analyses could revisit this approach with a larger dataset or alternative modeling strategies to better account for potential interactions.
+
+By using this model, we aim to better understand the factors that influence BMI and provide insights into potential public health interventions that could target lifestyle changes and socio-economic factors to reduce BMI and related health risks.
 
@@
 #| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+#| label: tbl-modelresults
+#| tbl-cap: "Summary statistics for variables in the NHANES dataset."
 
-library(rstanarm)
+# Load the saved linear model
+lm_model <- readRDS("/Users/hxw/marriage/models/lm_model.rds")
+# Tidy the model summary
+model_summary <- tidy(lm_model)
+# Extract R-squared value
+r_squared <- summary(lm_model)$r.squared
 
+# Add R-squared to the model summary table
+model_summary_with_r2 <- model_summary %>%
+  bind_rows(tibble::tibble(
+    term = "R-squared",
+    estimate = r_squared,
+    std.error = NA,
+    statistic = NA,
+    p.value = NA
+  ))
+
+# Print the model summary table using knitr::kable
+model_summary_with_r2 %>%
+  kable(caption = "Summary of the Linear Model for Log(BMI)")
 ```
@@
 ```{r}
-#| echo: false
-#| eval: true
+#| label: fig-predictor-bmi
+#| fig-cap: "Scatter plots of predictors vs. log(BMI) with fitted regression lines."
+#| fig.width: 8
+#| fig.height: 12
+
+# Scatter plot for Age vs. log(BMI)
+plot_age_bmi <- ggplot(nhanes_data, aes(x = Age, y = log(BMI))) +
+  geom_point(size = 0.3) +
+  geom_smooth(method = "lm", col = "red", se = FALSE) +
+  labs(title = "Age vs. log(BMI)", x = "Age", y = "log(BMI)") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 12), axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# Scatter plot for Gender vs. log(BMI)
+plot_gender_bmi <- ggplot(nhanes_data, aes(x = Gender, y = log(BMI))) +
+  geom_point() +
+  geom_smooth(method = "lm", col = "red", se = FALSE) +
+  labs(title = "Figure17: Gender vs. log(BMI)", x = "Gender", y = "log(BMI)") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+
+# Scatter plot for Poverty vs. log(BMI)
+plot_poverty_bmi <- ggplot(nhanes_data, aes(x = Poverty, y = log(BMI))) +
+  geom_point() +
+  geom_smooth(method = "lm", col = "red", se = FALSE) +
+  labs(title = "Figure18: Poverty vs. log(BMI)", x = "Poverty", y = "log(BMI)") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+
+# Scatter plot for SleepHrsNight vs. log(BMI)
+plot_sleep_bmi <- ggplot(nhanes_data, aes(x = SleepHrsNight, y = log(BMI))) +
+  geom_point() +
+  geom_smooth(method = "lm", col = "red", se = FALSE) +
+  labs(title = "Figure19: SleepHrsNight vs. log(BMI)", x = "SleepHrsNight", y = "log(BMI)") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+
+# Scatter plot for PhysActiveDays vs. log(BMI)
+plot_physactive_bmi <- ggplot(nhanes_data, aes(x = PhysActiveDays, y = log(BMI))) +
+  geom_point() +
+  geom_smooth(method = "lm", col = "red", se = FALSE) +
+  labs(title = "Figure20: Physical Active Days vs. log(BMI)", x = "PhysActiveDays", y = "log(BMI)") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+
+# Combine all plots into a single figure using patchwork
+library(patchwork)
+combined_plot <- (plot_age_bmi | plot_gender_bmi) / 
+                 (plot_poverty_bmi | plot_sleep_bmi) / 
+                 plot_physactive_bmi +
+  plot_annotation(
+    title = "Diagnostic and Predictor Relationships in the Linear Model",
+    caption = "Figure: Diagnostic and variable relationships from the linear model for log(BMI).",
+    theme = theme(plot.caption = element_text(hjust = 0.5, size = 10))
+  )
+
+# Display the combined plot
+combined_plot
 
@@
 
-Weaknesses and next steps should also be included.
+While the model results provide valuable insights into the relationship between log(BMI) and various predictor variables, there are some limitations that should be addressed in future analyses.
+One significant weakness is the relatively low R-squared value of 0.02335, indicating that the model only explains a small portion of the variance in BMI.
+This suggests that there are other factors, potentially unaccounted for in the model, that influence BMI.
+Although several predictors show statistically significant relationships with BMI, the explanatory power of the model remains limited.
+It is possible that additional variables, such as dietary habits, genetics, or environmental factors, could improve the model's ability to explain the variation in BMI.
+
+Another limitation is the potential for omitted variable bias.
+Despite including a range of relevant predictors, there may be other important factors that have not been incorporated into the model.
+For instance, socioeconomic status, mental health, or access to healthcare may play significant roles in determining BMI but were not included in the current analysis.
+Future models could benefit from a more comprehensive selection of predictor variables to provide a more holistic understanding of BMI variation.
+
+Additionally, the model assumes linear relationships between the predictors and BMI, which may not fully capture the complexities of the data.
+Interaction effects, such as between poverty and physical activity, could potentially reveal more nuanced relationships, but these were not included in the current model.
+The absence of interaction terms may have led to the underestimation of the impact of certain predictors, as the effect of one variable may depend on the level of another.
+Future analyses could explore interaction terms to assess whether these improve model fit and offer deeper insights into the factors that influence BMI.
+
+Moving forward, there are several steps that could be taken to address these weaknesses.
+First, the inclusion of additional predictors could improve the model's explanatory power.
+Collecting more detailed data on lifestyle, diet, or mental health factors would help provide a more complete picture of the determinants of BMI.
+Second, using a non-linear model or exploring transformations of the predictors might better capture the relationships between BMI and the explanatory variables.
+Finally, addressing the possibility of interaction effects and testing different model specifications could enhance the robustness of the results.
+This could include experimenting with non-parametric models, such as random forests or gradient boosting machines, to better handle the complexities of the data.
+By expanding the scope of the analysis and refining the model, future work could yield more precise estimates and offer more actionable insights for public health interventions.
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+The analysis of linear regression assumptions shows that all conditions are met.
+The fitted versus residual plot (Figure 8) displays a null plot centered around zero, indicating that the linearity assumption is satisfied, as no discernible pattern exists.
+Additionally, the consistent spread of residuals across the fitted values confirms the constant error variance assumption.
+The absence of correlation or patterns suggests that the independence of errors is also satisfied.
+Both the fitted versus standardized residuals plot (Figure 9) and the predictor variables versus residuals plots (Figures 11 to 13) support these conclusions.
+The QQ plot (Figure 15) shows standardized residuals following a straight diagonal line, while the histogram (Figure 10) indicates a distribution close to ~N(0,1), confirming the normality assumption of errors.
+Lastly, the response variable versus fitted values plot (Figure 14) shows that observed values align with predicted values, suggesting that the model accurately predicts the response variable.
+Although the residual plots indicate that all regression assumptions are met, the predictor versus response plots (Figures 16 to 20) show weak correlations between predictor variables and log(BMI), with log(BMI) approximated by
 
 ```{r}
+#| echo: false
+#| label: fig-model-diagnostics
+#| fig-cap: "Diagnostic and Predictor Relationships in the Linear Model for log(BMI)."
+#| fig.width: 8
+#| fig.height: 12
+
+# Extract values for residuals and fitted values
+fitted_values <- fitted(lm_model)
+residual_values <- resid(lm_model)
+sresidual_values <- rstandard(lm_model)
+
+# Data for scatter plots
+scatter_data <- nhanes_data %>%
+  mutate(log_BMI = log(BMI))
+
+# Create each plot
+# 1. Fitted vs Residuals
+plot_fitted_residuals <- ggplot(data.frame(fitted_values, residual_values), 
+                                aes(x = fitted_values, y = residual_values)) +
+  geom_point(color = "blue", size = 0.3) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  labs(title = "Fitted vs Residuals", x = "Fitted Values", y = "Residuals") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 2. Fitted vs Standardized Residuals
+plot_fitted_standardized <- ggplot(data.frame(fitted_values, sresidual_values), 
+                                   aes(x = fitted_values, y = sresidual_values)) +
+  geom_point(color = "red", size = 0.3) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  labs(title = "Fitted vs Standardized Residuals", x = "Fitted Values", y = "Standardized Residuals") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 3. Standardized Residuals Histogram
+plot_residuals_hist <- ggplot(data.frame(sresidual_values), aes(x = sresidual_values)) +
+  geom_histogram(binwidth = 0.1, fill = "lightblue", color = "black") +
+  labs(title = "Histogram of Standardized Residuals", x = "Standardized Residuals", y = "Frequency") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 4. Residuals vs Poverty
+plot_residuals_poverty <- ggplot(data.frame(nhanes_data$Poverty, residual_values), 
+                                 aes(x = nhanes_data$Poverty, y = residual_values)) +
+  geom_point(color = "green", size = 0.3) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  labs(title = "Poverty vs Residuals", x = "Poverty Index", y = "Residuals") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 5. Residuals vs Age
+plot_residuals_age <- ggplot(data.frame(nhanes_data$Age, residual_values), 
+                             aes(x = nhanes_data$Age, y = residual_values)) +
+  geom_point(color = "orange", size = 0.3) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  labs(title = "Age vs Residuals", x = "Age", y = "Residuals") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 6. Residuals vs Gender
+plot_residuals_gender <- ggplot(data.frame(nhanes_data$Gender, residual_values), 
+                                aes(x = nhanes_data$Gender, y = residual_values)) +
+  geom_boxplot(fill = "gray") +
+  labs(title = "Gender vs Residuals", x = "Gender", y = "Residuals") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 7. Fitted vs Log(BMI)
+plot_fitted_logBMI <- ggplot(data.frame(fitted_values, log_BMI = scatter_data$log_BMI), 
+                             aes(x = fitted_values, y = log_BMI)) +
+  geom_point(color = "purple", size = 0.3) +
+  geom_abline(intercept = 0, slope = 1, color = "blue", linetype = "dashed") +
+  labs(title = "Fitted vs log(BMI)", x = "Fitted Values", y = "log(BMI)") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# 8. Q-Q Plot
+plot_qq <- ggplot(data = data.frame(std_resid = rstandard(lm_model)), aes(sample = std_resid)) +
+  stat_qq(color = "darkred", size = 0.3) +
+  stat_qq_line(color = "blue") +
+  labs(title = "Normal Q-Q Plot", x = "Theoretical Quantiles", y = "Standardized Residuals") +
+  theme_minimal() +
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+
+# Combine all plots into one big plot
+big_plot <- (
+  (plot_fitted_residuals | plot_fitted_standardized) /
+  (plot_residuals_hist | plot_residuals_poverty) /
+  (plot_residuals_age | plot_residuals_gender) /
+  (plot_fitted_logBMI | plot_qq)
+)
+
+# Display the combined plot
+big_plot
 

### 2024-12-03 scripts/00-simulate_data.R

@@ -1,52 +1,36 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates the dataset
+# Author: Sakura Hu
+# Date: 01 December 2024
+# Contact: Sakura.Hu@utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: The `dplyr` package must be installed
+# Any other information needed? Make sure you are in the `bmi` rproj
+
 
 
 #### Workspace setup ####
-library(tidyverse)
-set.seed(853)
+library(dplyr)
+set.seed(1009201917)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+# Simulating data for the predictors
+n <- 100  # Number of observations
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
+# Simulating values based on the provided data
+simulated_data <- data.frame(
+  BMI = rnorm(n, mean = 15, sd = 6),
+  Poverty = sample(0:5, n, replace = TRUE),
+  PhysActiveDays = sample(1:7, n, replace = TRUE),
+  # Simulating physical activity days (1-7 scale)
+  Age = sample(16:80, n, replace = TRUE),
+  # Simulating ages (16 to 80 years)
+  SleepHrsNight = sample(2:12, n, replace = TRUE),
[…]

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,89 +1,85 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated data
+# Author: Sakura Hu
+# Date: 01 December 2024
+# Contact: Sakura.Hu@utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites:
+# - The `tidyverse`, `testthat`, and `pointblank` package must be installed and loaded
+# - 00-simulate_data.R must have been run
+# Any other information needed? Make sure you are in the `bmi` rproj
 
 
 #### Workspace setup ####
+library(testthat)
+library(pointblank)
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
 
 
 #### Test data ####
+simulated_data <- read_csv("/Users/hxw/marriage/data/00-simulated_data/simulated_data.csv")
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 151 rows.")
-}
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
-}
+#### Test Suite ####
 
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
[…]

### 2024-12-03 scripts/03-clean_data.R

@@ -28,7 +28,8 @@ clean_data <- raw_data %>%
     !is.na(Age),
     !is.na(SleepHrsNight),
     !is.na(Gender)
-  )
+  ) %>%
+  distinct()  # Remove duplicate rows
 
 #### Save data ####
 write_parquet(clean_data, "data/02-analysis_data/clean_data.parquet")

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -1,69 +1,85 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the analysis data
+# Author: Sakura Hu
+# Date: 01 December 2024
+# Contact: Sakura.Hu@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+# - The `arrow`, `testthat`, and `pointblank` package must be installed and loaded
+# - 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `bmi` rproj
 
 
 #### Workspace setup ####
-library(tidyverse)
 library(testthat)
+library(pointblank)
+library(arrow)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+analysis_data <- read_parquet("/Users/hxw/marriage/data/02-analysis_data/clean_data.parquet")
+
+
+
+#### Test Suite ####
+
+# 1. Test for Missing Values in Key Columns using pointblank
+test_that("No columns contain NA values", {
+  expect_equal(sum(is.na(analysis_data)), 0)
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+# 2. Test for Duplicates in the Dataset using testthat
+test_that("No duplicate rows exist", {
+  expect_equal(any(duplicated(analysis_data)), FALSE)
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
+# 3. Test if all 'BMI' are positive
+test_that("BMI values should be between 10 and 40", {
+  expect_true(all(analysis_data$BMI >= 0))  # Fixing the range here
 })
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
[…]

### 2024-12-03 paper/paper.qmd
some updates. still need: paper and datasheet

@@
 The dataset used in this analysis is derived from the US National Health and Nutrition Examination Survey (NHANES), version 2.1.0, published in July 2015.
+This version of the dataset includes survey results collected between October 2009 and December 2010.
 NHANES is a long-running study conducted by the US National Center for Health Statistics (NCHS) that has been gathering health and nutrition data since the early 1960s.
 Since 1999, approximately 5,000 individuals from various age groups have been interviewed annually in their homes and undergone health examinations at mobile examination centers (MEC).
-The dataset contains 10,000 observations and 76 variables.
+Two datasets in this package were considered for this analysis: NHANESraw, which is the original raw data, and NHANES, a resampled version of the NHANES data.
+NHANESraw contains the original survey data with 20,293 observations and additional variables describing the sample weighting scheme, while NHANES is a simplified version with 10,000 resampled observations to account for oversampling effects.
+NHANES is used in this analysis due to its ability to reduce the potential biases from the complex survey design in NHANESraw.
+Additional details about this choice are provided in Appendix A.
 The data used here was originally compiled by Michelle Dalrymple from Cashmere High School and Chris Wild from the University of Auckland for educational purposes.
@@
 After cleaning the missing values in the dataset, 3,573 observations remained.
-The dataset was prepared, cleaned, and analyzed using R (R Core Team, 2022) with the following libraries: opendatatoronto (Gelfand, 2022) for accessing the data, tidyverse (Wickham et al., 2019), dplyr (Wickham et al., 2023) for data manipulation, and ggplot2 (Wickham, 2016) for visualizations.
-Additionally, knitr (Xie, 2023a) was used for report generation, and styler (Müller et al., 2024) ensured the R code was properly styled.
+
+The dataset was prepared, cleaned, and analyzed using R [@citeR] with the following libraries: tidyverse [@tidyverse] and dplyr [@dplyr] for data manipulation, ggplot2 [@ggplot2] and patchwork [@patchwork] for visualizations, and broom [@broom] for model summaries.
+The arrow [@arrow] library was used for efficient data storage and retrieval, while knitr [@knitr] facilitated report generation.
+The NHANES package [@nhanes] provided access to the dataset, and styler [@styler] was employed to ensure well-structured R code.
+Additionally, testthat [@testthat] and pointblank [@pointblank] were utilized for data validation and testing.
 
@@
 summary_table %>%
-  kable(caption = "Summary statistics for variables in the NHANES dataset.")
+  kable()
 ```
@@
 ```{r}
+#| warning: false
+#| message: false
 #| label: fig-bmi-logbmi
@@
 # Figure 1: BMI and log(BMI)
-figure_bmi <- (hist_bmi | hist_log_bmi) +
-  plot_annotation(caption = "Figure 1: Distributions of BMI and log(BMI) in the NHANES dataset.",
-                  theme = theme(plot.caption = element_text(hjust = 0.5, size = 12)))
+figure_bmi <- (hist_bmi | hist_log_bmi)
 figure_bmi
@@
 ```{r}
+#| warning: false
+#| message: false
 #| label: fig-predictor-distributions
@@
 ```{r}
+#| warning: false
+#| message: false
 #| echo: false
@@
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
 #| label: fig-predictor-bmi
 #| fig-cap: "Scatter plots of predictors vs. log(BMI) with fitted regression lines."
+#| fig-subcap: ["Age vs. log(BMI)","Gender vs. log(BMI)", "Poverty vs. log(BMI)", "SleepHrsNight vs. log(BMI)","Physical Active Days vs. log(BMI)"]
+#| layout-ncol: 3
 #| fig.width: 8
@@
   geom_smooth(method = "lm", col = "red", se = FALSE) +
-  labs(title = "Age vs. log(BMI)", x = "Age", y = "log(BMI)") +
+  labs(x = "Age", y = "log(BMI)") +
   theme_minimal() +
-  theme(plot.title = element_text(size = 12), axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
 
-# Scatter plot for Gender vs. log(BMI)
+# Box plot for Gender vs. log(BMI)
 plot_gender_bmi <- ggplot(nhanes_data, aes(x = Gender, y = log(BMI))) +
-  geom_point() +
-  geom_smooth(method = "lm", col = "red", se = FALSE) +
-  labs(title = "Figure17: Gender vs. log(BMI)", x = "Gender", y = "log(BMI)") +
+  geom_boxplot(fill = "lightblue", color = "black") +  # Box plot
+  labs(x = "Gender", y = "log(BMI)") +
   theme_minimal() +
-  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
 
@@
 plot_poverty_bmi <- ggplot(nhanes_data, aes(x = Poverty, y = log(BMI))) +
-  geom_point() +
+  geom_point(size = 0.3) +
   geom_smooth(method = "lm", col = "red", se = FALSE) +
-  labs(title = "Figure18: Poverty vs. log(BMI)", x = "Poverty", y = "log(BMI)") +
+  labs(x = "Poverty", y = "log(BMI)") +
   theme_minimal() +
-  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
 
@@
 plot_sleep_bmi <- ggplot(nhanes_data, aes(x = SleepHrsNight, y = log(BMI))) +
-  geom_point() +
+  geom_point(size = 0.3) +
   geom_smooth(method = "lm", col = "red", se = FALSE) +
-  labs(title = "Figure19: SleepHrsNight vs. log(BMI)", x = "SleepHrsNight", y = "log(BMI)") +
+  labs(x = "SleepHrsNight", y = "log(BMI)") +
   theme_minimal() +
-  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
 
@@
 plot_physactive_bmi <- ggplot(nhanes_data, aes(x = PhysActiveDays, y = log(BMI))) +
-  geom_point() +
+  geom_point(size = 0.3) +
   geom_smooth(method = "lm", col = "red", se = FALSE) +
-  labs(title = "Figure20: Physical Active Days vs. log(BMI)", x = "PhysActiveDays", y = "log(BMI)") +
+  labs(x = "PhysActiveDays", y = "log(BMI)") +
   theme_minimal() +
-  theme(plot.title = element_text(size = 14), axis.title = element_text(size = 12), axis.text = element_text(size = 10))
+  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
 
-# Combine all plots into a single figure using patchwork
-library(patchwork)
-combined_plot <- (plot_age_bmi | plot_gender_bmi) / 
-                 (plot_poverty_bmi | plot_sleep_bmi) / 
-                 plot_physactive_bmi +
-  plot_annotation(
-    title = "Diagnostic and Predictor Relationships in the Linear Model",
-    caption = "Figure: Diagnostic and variable relationships from the linear model for log(BMI).",
-    theme = theme(plot.caption = element_text(hjust = 0.5, size = 10))
-  )
-
-# Display the combined plot
-combined_plot
+plot_age_bmi
+plot_gender_bmi
+plot_poverty_bmi
+plot_sleep_bmi
+plot_physactive_bmi
 
@@
 
-## First discussion point {#sec-first-point}
+## What is done in this paper? {#sec-first-point}
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+1.5 page This paper explores the relationship between Body Mass Index (BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
+The analysis is performed using a linear regression model, which allows us to estimate how each of these predictors influences BMI, as measured by its log-transformed values.
+The dataset used for this study is the cleaned data from the US National Health and Nutrition Examination Survey (NHANES), which contains a broad range of health-related information from a representative sample of the U.S.
+population.
 
-## Second discussion point
+The model aims to quantify the impact of each predictor on BMI while controlling for the influence of other variables.
+The regression analysis reveals significant relationships between BMI and all the predictors considered, with some factors having a negative impact (e.g., poverty, physical activity) and others having a positive one (e.g., age, sleep hours, gender).
+This model sheds light on the ways in which various lifestyle choices and demographic factors may contribute to BMI variation across different segments of the population.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+The model used in this study, a linear regression model, is a fundamental yet powerful tool that helps to identify the strength and direction of the relationships between predictors and BMI.
+The results provide a valuable starting point for understanding how changes in lifestyle and demographic factors may affect BMI.
+However, while the model is useful, it is not without its limitations.
+For instance, it assumes that the relationships between the predictors and BMI are linear, which may not always be the case.
+Additionally, the low R-squared value suggests that other important factors influencing BMI may not have been included in the model.
 
-## Third discussion point
+## What is something that we learn about the world?
+
+1.5 page One of the key findings from this paper is that poverty is negatively correlated with BMI, and the relationship is statistically significant.
+The negative coefficient for the poverty variable suggests that individuals in poverty tend to have higher BMI, on average, than those with higher income levels.
+This result is consistent with a growing body of literature that links lower socioeconomic status to obesity and poor health outcomes.
+It may seem counterintuitive at first—since poverty is often associated with limited access to healthy foods and exercise—but the correlation can be explained by several factors.
+
+In many low-income communities, the availability of affordable healthy food options is limited, leading individuals to rely on cheaper, calorie-dense foods that contribute to weight gain.
+Additionally, individuals in poverty may face multiple barriers to physical activity, including the lack of access to safe recreational spaces or the time and energy needed to engage in exercise, due to long working hours or other stressors.
+Furthermore, the high cost of healthcare and medical services in lower-income populations may prevent individuals from seeking preventative care and managing conditions like obesity.
+Thus, this finding underscores the importance of addressing socioeconomic disparities as part of efforts to combat obesity and improve public health.
+
+Moreover, this finding highlights the need for policy interventions that promote access to healthy food and physical activity in low-income communities.
+It also suggests that any interventions aimed at reducing BMI must consider not just individual behaviors, but the broader socioeconomic context in which these behaviors occur.
+Policymakers should prioritize interventions that reduce the barriers to healthy living for individuals in poverty, such as improving access to nutritious food, increasing public health education, and providing community resources for physical activity.
+
+## What is another thing that we learn about the world?
+
+1.5 page Another key takeaway from this paper is that sleep duration has a significant negative correlation with BMI, suggesting that individuals who get more sleep tend to have lower BMI.
+This relationship is in line with previous research that has examined the link between sleep and obesity.
+The coefficient for sleep hours per night shows that for each additional hour of sleep, BMI decreases slightly, indicating that sleep plays a role in regulating body weight.
+This finding has important implications for public health, as sleep duration is a modifiable lifestyle factor that could be targeted in weight management programs.
+
+The relationship between sleep and BMI can be explained through several mechanisms.
+Poor sleep has been shown to disrupt the body's metabolism, leading to an increase in appetite, particularly for high-calorie foods.
+Sleep deprivation also affects the hormones that regulate hunger and satiety, increasing the production of ghrelin (the hunger hormone) while decreasing the production of leptin (the satiety hormone).
+These changes can lead to overeating and, consequently, weight gain.
+Furthermore, insufficient sleep can lead to fatigue, reducing the likelihood of physical activity and further contributing to weight gain.
+Therefore, improving sleep hygiene and encouraging sufficient sleep may serve as an effective strategy for reducing BMI and addressing obesity.
+
+This result also emphasizes the importance of taking a holistic approach to health.
+In addition to focusing on diet and physical activity, interventions aimed at improving sleep quality could be a key component in the prevention and treatment of obesity.
+Public health campaigns that educate individuals about the importance of sleep, along with strategies to improve sleep hygiene (e.g., creating a conducive sleep environment, avoiding caffeine, establishing regular sleep routines), could complement existing efforts to promote healthy eating and physical activity.
 
@@
 
-# Additional data details
+# Additional data details {#sec-data-details}
+
+## Data Justication
+The NHANES_raw dataset provides a comprehensive collection of data from the American National Health and Nutrition Examination Surveys (NHANES), including 20,293 observations spanning 75 variables.
+This dataset includes additional variables that describe the sample weighting scheme employed to account for the complex survey design.
+However, despite its breadth and richness, NHANES_raw introduces complexities in analysis due to the oversampling of certain subpopulations, such as racial minorities.
+This sampling approach necessitates the use of survey weights and other design-specific parameters to obtain unbiased estimates and valid statistical inferences.
+
+Naïve analysis of NHANES_raw—without accounting for the sample design and weights—can lead to significant biases and erroneous conclusions.
+For instance, the racial composition in NHANES_raw does not represent the true demographic distribution of the U.S.
+population due to oversampling adjustments.
+As a result, researchers must account for these weights in any analysis to avoid overstating significance levels and generating inaccurate results.
+This makes NHANES_raw unsuitable for straightforward analysis in contexts where the primary goal is to demonstrate simple statistical relationships, especially for educational purposes.
+
+In contrast, the NHANES dataset, which is a resampled subset of NHANES_raw, addresses the complexities associated with the oversampling design.
+With 10,000 observations and the same 75 variables, NHANES is simplified to approximate a simple random sample from the U.S.
+population.
+This resampling process removes the need for researchers to manually account for the oversampling effects, enabling analyses that are easier to interpret and less prone to methodological errors for educational purposes.
+
+The decision to use NHANES in this paper was driven by its appropriateness for demonstrating relationships between body mass index (BMI) and lifestyle, poverty, age, and gender.
+NHANES allows for clear and reliable analyses without requiring specialized expertise in survey design or sampling weights, making it ideal for this study’s educational focus.
+The dataset enables meaningful exploration of public health questions while minimizing the risk of misinterpretation due to unaddressed biases in the sampling framework.
+
+It is important to acknowledge that NHANES is adapted for educational purposes and is not intended for formal research.
+Researchers conducting advanced studies should rely on the original NHANES_raw data and adhere to the prescribed sampling and weighting procedures to ensure the validity of their findings.
+Future research could extend the current analysis by using NHANES_raw in combination with survey weighting techniques to explore population-level health trends and disparities with greater accuracy.
+
+# Surveys, Sampling, and Observational Data {#sec-sampling-details}
 
 # Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-
-```
 
@@
 #| fig-cap: "Diagnostic and Predictor Relationships in the Linear Model for log(BMI)."
-#| fig.width: 8
-#| fig.height: 12
+#| fig-subcap: ["Fitted vs Residuals", "Fitted vs Standardized Residuals", "Histogram of Standardized Residuals", "Poverty vs Residuals", "Age vs Residuals", "Gender vs Residuals", "Fitted vs log(BMI)", "Normal Q-Q Plot"]
+#| layout-ncol: 4
+#| fig.width: 12
+#| fig.height: 18
 
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  labs(title = "Fitted vs Residuals", x = "Fitted Values", y = "Residuals") +
+  labs(x = "Fitted Values", y = "Residuals") +
   theme_minimal() +
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  labs(title = "Fitted vs Standardized Residuals", x = "Fitted Values", y = "Standardized Residuals") +
+  labs(x = "Fitted Values", y = "Standardized Residuals") +
   theme_minimal() +
@@
   geom_histogram(binwidth = 0.1, fill = "lightblue", color = "black") +
-  labs(title = "Histogram of Standardized Residuals", x = "Standardized Residuals", y = "Frequency") +
+  labs(x = "Standardized Residuals", y = "Frequency") +
   theme_minimal() +
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  labs(title = "Poverty vs Residuals", x = "Poverty Index", y = "Residuals") +
+  labs(x = "Poverty Index", y = "Residuals") +
   theme_minimal() +
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  labs(title = "Age vs Residuals", x = "Age", y = "Residuals") +
+  labs(x = "Age", y = "Residuals") +
   theme_minimal() +
@@
   geom_boxplot(fill = "gray") +
-  labs(title = "Gender vs Residuals", x = "Gender", y = "Residuals") +
+  labs(x = "Gender", y = "Residuals") +
   theme_minimal() +
@@
   geom_abline(intercept = 0, slope = 1, color = "blue", linetype = "dashed") +
-  labs(title = "Fitted vs log(BMI)", x = "Fitted Values", y = "log(BMI)") +
+  labs(x = "Fitted Values", y = "log(BMI)") +
   theme_minimal() +
@@
   stat_qq_line(color = "blue") +
-  labs(title = "Normal Q-Q Plot", x = "Theoretical Quantiles", y = "Standardized Residuals") +
+  labs(x = "Theoretical Quantiles", y = "Standardized Residuals") +
   theme_minimal() +
@@
 
-# Combine all plots into one big plot
-big_plot <- (
-  (plot_fitted_residuals | plot_fitted_standardized) /
-  (plot_residuals_hist | plot_residuals_poverty) /
-  (plot_residuals_age | plot_residuals_gender) /
-  (plot_fitted_logBMI | plot_qq)
-)
-
-# Display the combined plot
-big_plot
+plot_fitted_residuals
+plot_fitted_standardized
+plot_residuals_hist
+plot_residuals_poverty
+plot_residuals_age
+plot_residuals_gender
+plot_fitted_logBMI
+plot_qq
 

### 2024-12-04 other/datasheet/datasheet_template.qmd
almost finished

---
title: "Datasheet for NHANES dataset'"
author: 
  - Sakura Hu
thanks: "Code and data are available at: https://github.com/xycww/BMI/tree/main."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: datasheetreference.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The National Health and Nutrition Examination Survey (NHANES) was created to assess the health and nutritional status of adults and children in the United States. The survey combines both interviews and physical examinations to gather comprehensive health data. The primary task of NHANES is to provide vital statistics on the nation’s health, enabling public health experts, policymakers, and researchers to track trends in nutrition, health behaviors, and the prevalence of chronic diseases. The resampled version of NHANES data, which is utilized in this analysis, has been adapted specifically for educational purposes. This version of the data corrects for the oversampling of certain populations (e.g., racial minorities) to ensure a more accurate representation of the U.S. population. The aim of this adjustment is to make the dataset suitable for educational use, enabling students and researchers to analyze and learn from it while avoiding potential biases introduced by the original survey's complex sampling methods. This resampling version helps simplify the dataset and facilitates learning without compromising the integrity of the data collection process.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The NHANES dataset was created by the National Center for Health Statistics (NCHS), which is part of the Centers for Disease Control and Prevention (CDC). NCHS is responsible for producing and maintaining vital health statistics in the United States. The resampled data was assembled by Michelle Dalrymple of Cashmere High School and Chris Wild of the University of Auckland, New Zealand for educational purposes.

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset itself is a public health initiative and does not have a specific grant associated with its creation. Instead, it is part of the ongoing federal program aimed at monitoring the health and nutritional status of the U.S. population.

4. *Any other comments?*
    - No

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instances in the National Health and Nutrition Examination Survey (NHANES) dataset represent individuals (people) from the non-institutionalized civilian population of the United States.

2. *How many instances are there in total (of each type, if appropriate)?*
	- The NHANES raw data contains 20,293 instances, while the NHANES resampled data contains 10,000 instances.

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The NHANES dataset is a sample of the larger set, which is the non-institutionalized civilian resident population of the United States. The dataset does not include all possible instances of this population, but instead employs a complex survey design that uses multistage probability sampling to select participants. The larger set includes all individuals in the U.S. who live in households, excluding institutionalized populations like those in prisons or long-term care facilities.

	The sample is designed to be representative of the larger U.S. population, but with oversampling of certain subpopulations such as racial minorities, low-income individuals, and the elderly. These oversampling strategies are employed to ensure that there is sufficient data to generate reliable estimates for these groups, which may be underrepresented in a simple random sample. For example, the NHANES oversamples non-Hispanic Black, Hispanic, low-income White persons, and individuals aged 80 and older.

	To make the sample representative of the entire U.S. population, weights are applied to account for the oversampling and to adjust for differential probabilities of selection. This allows the data to be treated as if it were a simple random sample, and the weighted results can be generalized to the broader population. The representativeness of the sample is verified through the use of these weights and by ensuring that the sample covers various geographic regions of the U.S., including both metropolitan and non-metropolitan areas. Additionally, the NHANES sampling design has been rigorously tested and adjusted to ensure that it accurately reflects the population in terms of demographic factors.

4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance of the raw data consists of 76 variables. Variables include study variables such as participant identifier, demographic variables such as age, gender, race, as well as physical measurements such as weight and height. It also includes health data like sleep hours, cholesterol level, and lifestyle factors like smoking and alcohol consumption.

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- There is no single, explicit label or target associated with each instance, as the dataset contains a wide range of variables that may be used depending on the specific analysis.

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- The NHANES dataset contains missing data, which can be categorized as either unit nonresponse or component/item nonresponse. Unit nonresponse occurs when an individual selected to participate in the survey does not respond during either the interview or examination phase. For example, during the 2009-2010 cycle, of the 13,272 individuals eligible for participation, only 10,537 completed the household interview, leading to an interview nonresponse rate of 21%. Furthermore, of the interviewed participants, only 10,253 participated in the Medical Examination Center (MEC) examination, contributing to an additional 2% of nonresponse during the examination phase. This nonresponse is addressed by applying sample weights that adjust for the nonresponse. Component/item nonresponse refers to missing data from specific survey components, such as not all participants opting to complete a particular health examination (e.g., a blood pressure measurement). Additionally, NHANES uses specific codes for missing values, such as a period (.) for numeric variables and blank spaces for character variables. Responses like "refused" or "don't know" are also treated as missing and are assigned specific codes (e.g., 7, 77, or 777 for "refused" and 9, 99, or 999 for "don't know"). These should also be treate as missing data to avoid distorting analysis results.

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- There are no relationships between individual instances mode explicitly in the NHANES dataset.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- there are no formal recommendations for typical splits such as training, development/validation, and testing. However, given the structure and design of NHANES, there are important considerations for subsetting and combining data that influence how data is prepared for analysis. Since NHANES uses a complex, multi-stage sampling design, any analysis must account for the sampling weights and stratification to avoid bias.

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- One prominent issue is nonresponse bias, which occurs when certain individuals or groups fail to participate in the survey or specific components of the survey (e.g., medical examinations). This nonresponse can introduce bias if the missing data is systematically related to key variables. For example, older individuals or those with lower income may be less likely to respond, resulting in underrepresentation of these groups. NHANES mitigates this through the use of sampling weights that adjust for nonresponse, but analysts must still carefully account for this in their analysis. 
	Another source of noise is measurement error. NHANES collects data through a combination of self-reported surveys and physical examinations. Self-reported data, such as dietary intake, physical activity, or smoking habits, are prone to recall bias and social desirability bias. These errors can introduce variability and reduce the reliability of the data. On the other hand, while data from physical examinations and laboratory tests are generally more reliable, they are not immune to technical or procedural errors during measurement or data entry.

10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The NHANES dataset itself is self-contained and does not link to or otherwise rely on external resources.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The NHANES dataset does not contain data that might be considered confidential in the publicly available versions.

12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The NHANES dataset does not contain data that, if viewed directly, would generally be considered offensive, insulting, or threatening. However, it includes sensitive health-related information such as data on weight, body mass index (BMI), chronic diseases, substance use (e.g., smoking, alcohol, and drug use), mental health, sexual history, and socioeconomic status. While this data is anonymized and presented in an aggregated form, its content could potentially cause discomfort, anxiety, or distress to certain individuals, particularly if the topics touch on personal or stigmatized experiences.

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Yes, the NHANES dataset identifies several subpopulations based on demographic and socioeconomic characteristics.
	- Age is recorded in years and categorized into decades. The dataset includes participants across a wide age range, with individuals aged 80 and over intentionally oversampled to ensure adequate representation of this subgroup.
	- Race is categorized as Mexican, Hispanic, White, Black, Asian, or Other. Non-Hispanic Black persons and Hispanic persons are intentionally oversampled to improve the reliability and precision of estimates for these subpopulations.
	- Income is categorized using a poverty ratio, which reflects a range of socioeconomic statuses, with specific attention given to low-income white groups.
	- Gender is categorized as male and female, with the dataset typically having an approximately equal distribution of males and females.

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, it is not possible to identify individuals from the dataset

15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The NHANES dataset contains data that could be considered sensitive in several ways. This includes data on race and ethnicity, which are categorized as Mexican, Hispanic, White, Black, Asian, or Other. While these categories are used for public health research purposes, their inclusion may be viewed as sensitive because such data could potentially be misused or misinterpreted outside its intended context.

	The dataset also includes socioeconomic data, such as household income levels and poverty ratios. These variables reveal participants' financial statuses, which can be considered private and sensitive. Additionally, health-related data, including medical diagnoses, physical measurements (e.g., body mass index, blood pressure), and laboratory test results, comprise a significant portion of the dataset. These health metrics may reveal personal and potentially stigmatizing information about an individual's physical or mental health.

	Furthermore, the dataset includes biometric data such as weight, height, and blood test results. While NHANES does not include genetic data or government identification numbers (such as Social Security numbers), the presence of health and demographic variables may still pose confidentiality risks if improperly handled. However, strict measures are in place to protect participant privacy, including anonymization, ethical review processes, and federal confidentiality protections.

16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data associated with each instance in the NHANES dataset was primarily acquired through both directly observable measurements and self-reported survey responses. For instance, health data such as blood pressure, body mass index (BMI), and laboratory test results were directly measured during health examinations conducted at mobile examination centers (MECs). These direct observations are objective and typically subject to standardized procedures to ensure accuracy and consistency.

	In contrast, demographic and lifestyle information (e.g., age, gender, race, smoking habits, physical activity) were self-reported by participants through structured interviews. This data is subjective and relies on the accuracy and honesty of the respondents.

	To enhance the reliability of the dataset and minimize biases, the self-reported data was verified and validated in several ways. First, sample weights are applied to correct for unequal probabilities of selection and nonresponse. For example, oversampling of certain subpopulations, like racial minorities and low-income groups, was performed, and the sample weights adjust for these oversampling techniques.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Health Examinations and Laboratory Tests: Data such as blood pressure, height, weight, BMI, and other health measurements were collected during in-person visits to mobile examination centers (MECs). These centers are equipped with specialized medical equipment to directly measure participants’ health metrics. The collection of these data points is validated by well-established clinical protocols and the use of calibrated equipment to ensure the accuracy of the measurements.
	- Survey Interviews: Participants also answered detailed surveys that included demographic, socioeconomic, and lifestyle-related questions. This data was gathered through structured interviews conducted by trained personnel using electronic devices such as tablets. The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors. For instance, if a participant was unable to understand or respond in English, interpreters were made available to facilitate communication. The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections. The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors. The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is a sample drawn from the larger U.S. civilian noninstitutionalized population, and the sampling strategy is specifically designed to ensure the sample is representative of the broader population.

	- Sample selection for NHANES followed 4 stages:
	Primary Sampling Units (PSUs): In the first stage, primary sampling units, which are typically counties or groups of contiguous counties, are selected with probability proportional to size (PPS). This means that PSUs with larger populations have a higher probability of being selected. This approach helps ensure that the sample reflects the distribution of the population, with oversampling occurring for certain groups of interest, such as racial minorities, to improve the reliability of estimates for these subgroups.

Segmentation: After selecting the PSUs, the next stage involves dividing the selected PSUs into smaller segments, typically geographic units such as city blocks. These segments are then chosen using PPS to ensure an adequate representation of different population groups.

Dwelling Units (DUs): The third stage involves selecting dwelling units (households) within the chosen segments. In areas with higher concentrations of specific groups, such as low-income or minority populations, these households are selected at a higher rate to ensure proper representation of these groups.

Selection of Individuals: In the final stage, individuals are randomly selected from within the households. The selection is done within designated age, sex, and race/ethnicity subdomains to achieve a balance across these demographic characteristics. This step ensures that the sample includes a diverse range of individuals and that subgroups, such as the elderly or certain racial/ethnic populations, are adequately represented.

- To ensure that specific demographic subgroups are sufficiently represented, NHANES uses oversampling techniques. For example, non-Hispanic black, Hispanic, and low-income white individuals, as well as those aged 80 and older, are oversampled. This oversampling allows for more precise estimates for these groups, which may otherwise be underrepresented in a simple random sample.

- Due to the complex sampling design, sample weights are applied to adjust for unequal probabilities of selection and to account for nonresponse. These weights allow analysts to produce nationally representative estimates, as they correct for the oversampling of certain subgroups and for any nonresponse bias.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The data collection for the NHANES dataset was carried out by a team of professionals and experts under the guidance of the National Center for Health Statistics (NCHS), which is part of the Centers for Disease Control and Prevention (CDC). The team responsible for data collection consisted of field interviewers, medical personnel, and technicians who worked in the mobile examination centers (MECs) as well as in the field during household interviews. They were compensated with salaries or hourly wages based on their roles and responsibilities.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data used in this paper was collected as part of the 2009-2010 NHANES survey cycle, and it matches the creation timeframe of the data associated with the instances.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Yes, ethical review processes were conducted for the NHANES dataset. The NHANES protocol was developed and reviewed to be in compliance with the U.S. Department of Health and Human Services (HHS) Policy for Protection of Human Research Subjects, as outlined in 45 CFR part 46, which can be accessed at [HHS Policy for Protection of Human Research Subjects](http://www.hhs.gov/ohrp/humansubjects/guidance/45cfr46.html).

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- I did not collect the data, I obtain it through the NHANES package.

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*

	![consent form](/Users/hxw/marriage/other/datasheet/consent.png)

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- yes, and it is shown in the consent form provided.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- yes, and this information is shown at [participant FAQ](https://www.cdc.gov/nchs/nhanes/participant/participant-faq.htm).

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No.

12. *Any other comments?*
	- No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- NHANES uses specific codes for "refused" and "don't know" responses, assigning values such as 7, 77, or 777 for refusals, and 9, 99, or 999 for "don't know" responses.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- No
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- No
4. *Any other comments?*
	- No

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, the NHANES dataset has been used extensively in a variety of tasks related to public health research and analysis. Since its inception, the dataset has been used to assess the health and nutritional status of the U.S. population, providing valuable insights into a wide range of health indicators, including obesity, diabetes, cardiovascular diseases, and other chronic conditions. Researchers have used NHANES data to analyze the prevalence of different health conditions, identify risk factors, evaluate the impact of lifestyle choices (such as diet, physical activity, and smoking) on health outcomes, and inform public health policies.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Some of the product can be found [here](https://www.cdc.gov/nchs/nhanes/nhanes_products.htm).

3. *What (other) tasks could the dataset be used for?*
	- The NHANES dataset offers a wide range of potential uses beyond its current applications in health research. It can be used for longitudinal studies to track health trends, predictive modeling for disease prevention, and analysis of health disparities related to socioeconomic factors. Additionally, the dataset is valuable for exploring the relationship between diet and chronic disease, studying environmental health impacts, and evaluating medication use. It can also be applied in machine learning for disease prediction and in public health interventions aimed at changing health behaviors. Overall, NHANES supports diverse research areas, from epidemiology to policy simulation.

4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No

5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The NHANES dataset should not be used for any tasks that involve attempting to identify individuals or establishments, as doing so would violate confidentiality agreements and ethical guidelines. Specifically, the dataset should not be used for tasks such as re-identifying individuals, linking it with other datasets that contain personally identifiable information, or attempting to assess the effectiveness of privacy protection methodologies. The data is intended solely for statistical reporting and analysis, and any attempt to discern the identity of participants or establishments could lead to legal, ethical, and privacy concerns. Users must also ensure that the dataset is not used in ways that compromise the confidentiality of the individuals or establishments involved.

6. *Any other comments?*
	- No

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the NHANES dataset is publicly available and can be distributed to third parties. It is released by the National Center for Health Statistics (NCHS) under the Centers for Disease Control and Prevention (CDC) for public use. The dataset is accessible via the CDC's NHANES website, where anyone can download it for statistical analysis and research purposes. However, there are specific guidelines on how the data should be used, including the restriction that it should only be used for statistical reporting and analysis and should not be linked to individually identifiable data.

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The data can be downloaded directly from the NHANES page on the CDC official website

3. *When will the dataset be distributed?*
	- The NHANES 2009-2010 data were made available after the data collection period ended

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- Data Use Agreement can be found at [this website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- DLicensing terms and fees associated with restriction can be found at [the website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No

7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The NHANES dataset is supported, hosted, and maintained by the National Center for Health Statistics (NCHS), which is part of the Centers for Disease Control and Prevention (CDC).

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact NHANES staff by calling 1 (800) 232-4636

3. *Is there an erratum? If so, please provide a link or other access point.*
	- No

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Updated will be informed in the CDC official website.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- There is no limitation on this.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older version of dataset is hosted by CDC, and any updated will be informed in the CDC official website.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- If someone wants to contribut, they are welcome to contact NHANES staffs.

8. *Any other comments?*
	- No

\newpage

# References

### 2024-12-04 paper/paper.qmd
almost finished

@@
 
-The dataset used in this analysis is derived from the US National Health and Nutrition Examination Survey (NHANES), version 2.1.0, published in July 2015.
+The dataset used in this analysis is derived from the US National Health and Nutrition Examination Survey (NHANES), version 2.1.0.
 This version of the dataset includes survey results collected between October 2009 and December 2010.
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The NHANES dataset aims to provide a comprehensive view of the health and nutritional status of the U.S.
+population, transforming real-world phenomena into structured data entries.
+The data collection process begins with the selection of a sample from the U.S.
+population using a complex, multistage probability sampling design.
+This ensures that the sample is representative of the civilian, non-institutionalized population, while also oversampling certain subgroups, such as racial minorities, to ensure sufficient data for subgroup analysis.
+Once selected, individuals are surveyed on various health and lifestyle factors, such as their eating habits, physical activity, medical conditions, and demographics.
+The participants are then examined in a Mobile Examination Center (MEC) where they undergo physical assessments, laboratory tests, and interviews.
+
+The process of measurement involves both self-reported data and direct observations.
+For example, data on an individual’s lifestyle habits, such as hours of physical activity, alcohol consumption, or smoking, is obtained through self-reports in interviews.
+These responses are recorded as variables in the dataset, and any missing values or refusals are appropriately coded.
+On the other hand, physical measurements like height, weight, blood pressure, and cholesterol levels are directly taken in the MEC using medical equipment.
+These physical measurements are then processed and entered into the dataset.
+For each individual, these variables represent their health status at a specific time, providing a snapshot that is used for statistical analysis.
+
+Importantly, NHANES also accounts for missing data, a common occurrence in surveys.
+Missing values may arise if a participant refuses to answer a particular question or does not undergo a specific examination.
+These missing values are systematically handled by assigning special codes such as a period (.) for numeric variables or blanks for character variables, ensuring that they are not treated as valid data.
+Furthermore, to mitigate potential bias due to missing data, adjustments are made using sample weights to produce national estimates that are representative of the U.S.
+population.
+
+In the case of variables related to health measurements, the data undergo further validation through the use of sampling weights and variance estimation to ensure that the final dataset accurately reflects the population’s health status.
+This process involves using the complex survey design parameters, such as the primary sampling unit (PSU) and strata, to adjust the data accordingly, so that analyses can account for oversampling of certain subpopulations and non-response during data collection.
+Thus, every entry in the dataset is an outcome of rigorous data collection methods, reflecting a specific health measure or lifestyle factor that has been transformed into a quantifiable variable, which can then be analyzed and used for public health research.
 
@@
 
-1.5 page This paper explores the relationship between Body Mass Index (BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
+page This paper explores the relationship between Body Mass Index (BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
 The analysis is performed using a linear regression model, which allows us to estimate how each of these predictors influences BMI, as measured by its log-transformed values.
@@
 
-1.5 page One of the key findings from this paper is that poverty is negatively correlated with BMI, and the relationship is statistically significant.
+One of the key findings from this paper is that poverty is negatively correlated with BMI, and the relationship is statistically significant.
 The negative coefficient for the poverty variable suggests that individuals in poverty tend to have higher BMI, on average, than those with higher income levels.
@@
 
-1.5 page Another key takeaway from this paper is that sleep duration has a significant negative correlation with BMI, suggesting that individuals who get more sleep tend to have lower BMI.
+Another key takeaway from this paper is that sleep duration has a significant negative correlation with BMI, suggesting that individuals who get more sleep tend to have lower BMI.
 This relationship is in line with previous research that has examined the link between sleep and obesity.
@@
 # Surveys, Sampling, and Observational Data {#sec-sampling-details}
+The National Health and Nutrition Examination Survey (NHANES) represents one of the most comprehensive and influential health datasets in the United States, providing a valuable resource for understanding the health and nutritional status of the U.S.
+population.
+Conducted by the National Center for Health Statistics (NCHS), NHANES gathers both interview and physical examination data, which are combined to produce estimates of the general population’s health, nutritional status, and related behaviors.
+The methodology behind the NHANES survey is complex and carefully designed to ensure that the data collected are representative of the U.S.
+civilian, non-institutionalized population.
+
+The target population of NHANES consists of the civilian, non-institutionalized population of the United States, including individuals of all ages.
+This broad and inclusive definition ensures that the data captured by NHANES reflect the health and nutritional status of nearly every demographic group in the country.
+However, as a complex survey design, NHANES also uses a stratified, multistage sampling approach to select participants, ensuring that certain subgroups, particularly those with greater health disparities, are adequately represented.
+To achieve this goal, NHANES selects a representative sample from all counties in the U.S.
+Each year, a new group of PSUs (Primary Sampling Units) is chosen, which typically consist of counties or groups of contiguous counties.
+A total of about 12,000 people participate in each two-year cycle.
+This sampling method incorporates differential probabilities of selection, ensuring that groups at higher risk of health issues or underrepresentation (e.g., racial minorities, elderly individuals) are more likely to be sampled.
+As a result, NHANES oversamples certain subgroups, such as non-Hispanic Black individuals, Hispanic individuals, and elderly individuals over the age of 80, to improve the precision and reliability of health estimates for these populations.
+
+The recruitment process for NHANES is critical to ensuring that the sample is representative and that response rates are maximized.
+The process begins by selecting households through a multi-stage sampling design.
+In the first stage, PSUs are chosen using probability proportional to size (PPS), ensuring that more populous areas are selected with higher likelihood.
+In the second stage, segments within the PSUs are selected—typically representing census blocks or other local geographic units.
+In the third stage, households within the segments are listed, and a sample of households is chosen.
+Finally, individuals are selected within these households, using a method that ensures the representation of key demographic characteristics such as age, sex, and race/ethnicity.
+On average, two participants are chosen per eligible household, which allows the survey to gather a substantial amount of data on family structures, as well as individual health outcomes.
+
+The sampling approach used by NHANES is probabilistic, which means that each person in the target population has a known, non-zero probability of being selected.
+This is in contrast to deterministic approaches, which might introduce bias by excluding certain groups or individuals from the sample.
+By employing a probabilistic method, NHANES ensures that its data can be generalized to the entire U.S.
+population, although care must be taken when analyzing smaller subgroups, given the smaller sample sizes in these categories.
+One of the trade-offs of this probabilistic sampling approach is the increased complexity of the survey design.
+Given the multi-stage sampling procedure, survey weights and variance estimation methods must be carefully applied during the data analysis phase to adjust for the unequal probabilities of selection and the clustering of respondents within geographic regions.
+These adjustments are necessary to avoid biased estimates, particularly when estimating health indicators for subgroups or when combining data across multiple survey cycles.
+
+Non-response is a common challenge in large-scale surveys like NHANES, and its handling is critical to ensuring that the data remain unbiased and representative.
+Non-response in NHANES can occur at both the unit (or sample person) level and the component (or item) level.
+Unit non-response refers to individuals who are selected to participate in the survey but either refuse to participate or fail to respond to any part of the survey (e.g., household interview or medical examination).
+In the 2009-2010 cycle, for example, of the 13,272 persons eligible to participate, 21% failed to complete the household interview, and a further 2% of those who completed the interview did not participate in the medical examination.
+These non-responses were adjusted for using sampling weights, which are designed to reflect the number of individuals in the population represented by each sample respondent.
+
+Component non-response, on the other hand, refers to missing data for specific questions or tests within the survey.
+For example, a respondent may refuse to have their blood pressure measured but complete all other examination components.
+NHANES addresses component non-response by treating missing values as missing and adjusting the weights accordingly.
+When analyzing the data, researchers are encouraged to evaluate the extent of missing data for their variables of interest and to apply reweighting or imputation techniques if necessary, particularly when more than 10% of the data for a given variable is missing.
+While NHANES employs rigorous methods to handle non-response, it remains a potential source of bias.
+Non-respondents may differ in key characteristics from respondents, such as age, gender, or health status.
+This is particularly true for elderly individuals or those with more severe health issues, who may be less likely to participate in the survey.
+Therefore, the results of NHANES should always be interpreted with caution, especially when analyzing specific subgroups or when drawing conclusions about less-represented populations.
+
+The NHANES questionnaire and data collection process are designed to capture a comprehensive range of health, nutritional, and demographic information.
+The questionnaire consists of multiple sections, including detailed questions on demographic characteristics (e.g., age, sex, race, income), health behaviors (e.g., smoking, alcohol consumption, physical activity), and medical history (e.g., chronic diseases, medication use).
+The questionnaire also covers dietary intake, which is crucial for understanding the population’s nutritional status.
+
+The questionnaire is administered during a household interview, which is followed by a physical examination at the Mobile Examination Centers (MEC).
+During the MEC visit, participants undergo a range of tests, including anthropometric measurements (e.g., height, weight, BMI), blood pressure measurements, and laboratory tests (e.g., blood, urine samples).
+The tests performed in the MEC allow for objective measurements of participants’ health, complementing the self-reported information collected during the interview.
+
+The NHANES questionnaire is continuously updated to reflect new public health concerns and emerging health trends.
+For example, over time, the survey has included questions related to emerging issues such as mental health, sleep patterns, and environmental exposures.
+However, the questionnaire also has limitations.
+For example, self-reported data on health behaviors like physical activity or dietary intake may be subject to recall bias, with participants underestimating or overestimating their behaviors.
+Additionally, some participants may be reluctant to report sensitive information, such as smoking or alcohol consumption, which can further skew the data.
+
+One of the major strengths of the NHANES methodology is its ability to provide nationally representative estimates of health and nutritional status across a wide range of demographic and geographic subgroups.
+By combining interviews with objective physical examinations and laboratory tests, NHANES offers a rich, multi-dimensional view of health in the U.S.
+population.
+The rigorous sampling and data collection procedures ensure that the data can be used for a wide variety of public health analyses, from assessing chronic disease prevalence to tracking health trends over time.
+
+However, NHANES also has several weaknesses.
+The most notable is the issue of non-response, particularly in certain subgroups (e.g., elderly individuals, people with poor health).
+While the survey adjusts for non-response using weights, there is always the possibility that the non-respondents differ systematically from the respondents, which could lead to biased estimates.
+Additionally, the reliance on self-reported data can introduce biases such as social desirability bias or recall bias, which can affect the accuracy of responses on health behaviors and lifestyle factors.
+
+Moreover, the fact that NHANES data are released in two-year cycles means that estimates for some subgroups may not be stable, particularly for rare health conditions or smaller demographic groups.
+Combining data across multiple years can help mitigate this issue, but it also introduces complexities in terms of data harmonization and analytic guidelines.
+
+In conclusion, NHANES provides a valuable and unique resource for understanding the health and nutritional status of the U.S.
+population.
+Its robust sampling methodology, comprehensive questionnaire, and use of both self-reported and objective health measures make it an indispensable tool for public health research.
+While the survey has several strengths, including its representativeness and ability to assess health trends over time, it also faces challenges related to non-response, data quality, and biases inherent in self-reported information.
+Researchers must be mindful of these issues when analyzing NHANES data, and apply appropriate statistical methods to account for potential biases.
+Nonetheless, NHANES remains a cornerstone of U.S.
+public health surveillance, providing critical insights into the health and well-being of the nation’s diverse population.
 
@@
 The analysis of linear regression assumptions shows that all conditions are met.
-The fitted versus residual plot (Figure 8) displays a null plot centered around zero, indicating that the linearity assumption is satisfied, as no discernible pattern exists.
+The fitted versus residual plot displays a null plot centered around zero, indicating that the linearity assumption is satisfied, as no discernible pattern exists.
 Additionally, the consistent spread of residuals across the fitted values confirms the constant error variance assumption.
 The absence of correlation or patterns suggests that the independence of errors is also satisfied.
-Both the fitted versus standardized residuals plot (Figure 9) and the predictor variables versus residuals plots (Figures 11 to 13) support these conclusions.
-The QQ plot (Figure 15) shows standardized residuals following a straight diagonal line, while the histogram (Figure 10) indicates a distribution close to ~N(0,1), confirming the normality assumption of errors.
-Lastly, the response variable versus fitted values plot (Figure 14) shows that observed values align with predicted values, suggesting that the model accurately predicts the response variable.
-Although the residual plots indicate that all regression assumptions are met, the predictor versus response plots (Figures 16 to 20) show weak correlations between predictor variables and log(BMI), with log(BMI) approximated by
+Both the fitted versus standardized residuals plot and the predictor variables versus residuals plots support these conclusions.
+The QQ plot shows standardized residuals following a straight diagonal line, while the histogram indicates a distribution close to ~N(0,1), confirming the normality assumption of errors.
+Lastly, the response variable versus fitted values plot shows that observed values align with predicted values, suggesting that the model accurately predicts the response variable.
+Although the residual plots indicate that all regression assumptions are met, the predictor versus response plots show weak correlations between predictor variables and log(BMI
 

### 2024-12-14 other/datasheet/datasheet_template.qmd
updatated datasheet

@@
   - Sakura Hu
-thanks: "Code and data are available at: https://github.com/xycww/BMI/tree/main."
+thanks: "Code and data are available at: https://github.com/xycww/BMI."
 date: today
@@
 format: pdf
+resource-paths: ["other/datasheet"]
 number-sections: true
@@
     - The National Health and Nutrition Examination Survey (NHANES) was created to assess the health and nutritional status of adults and children in the United States.
-The survey combines both interviews and physical examinations to gather comprehensive health data.
+The survey combines both interviews and physical examinations to gather comprehensive health data [@nhanes].
 The primary task of NHANES is to provide vital statistics on the nation’s health, enabling public health experts, policymakers, and researchers to track trends in nutrition, health behaviors, and the prevalence of chronic diseases.
-The resampled version of NHANES data, which is utilized in this analysis, has been adapted specifically for educational purposes.
-This version of the data corrects for the oversampling of certain populations (e.g., racial minorities) to ensure a more accurate representation of the U.S.
+The resampled version of NHANES data, which is utilized in this analysis, has been adapted specifically for educational purposes [@nhanes].
+This version of the data corrects for the oversampling of certain populations to ensure a more accurate representation of the U.S.
 population.
-The aim of this adjustment is to make the dataset suitable for educational use, enabling students and researchers to analyze and learn from it while avoiding potential biases introduced by the original survey's complex sampling methods.
+The aim of this adjustment is to make the dataset suitable for educational use, enabling students and researchers to analyze and learn from it while avoiding potential biases introduced by the original survey's complex sampling methods [@nhanes].
 This resampling version helps simplify the dataset and facilitates learning without compromising the integrity of the data collection process.
@@
 NCHS is responsible for producing and maintaining vital health statistics in the United States.
-The resampled data was assembled by Michelle Dalrymple of Cashmere High School and Chris Wild of the University of Auckland, New Zealand for educational purposes.
+The resampled data was assembled by Michelle Dalrymple of Cashmere High School and Chris Wild of the University of Auckland, New Zealand for educational purposes [@nhanes].
 
@@
 Please provide a description.*
-	- Each instances in the National Health and Nutrition Examination Survey (NHANES) dataset represent individuals (people) from the non-institutionalized civilian population of the United States.
+	- Each instances in the National Health and Nutrition Examination Survey (NHANES) dataset represent individuals (people) from the non-institutionalized civilian population of the United States [@nhanes].
 
@@
 These oversampling strategies are employed to ensure that there is sufficient data to generate reliable estimates for these groups, which may be underrepresented in a simple random sample.
-For example, the NHANES oversamples non-Hispanic Black, Hispanic, low-income White persons, and individuals aged 80 and older.
+For example, the NHANES oversamples non-Hispanic Black, Hispanic, low-income White persons, and individuals aged 80 and older [@sample].
 
@@
 This allows the data to be treated as if it were a simple random sample, and the weighted results can be generalized to the broader population.
-The representativeness of the sample is verified through the use of these weights and by ensuring that the sample covers various geographic regions of the U.S., including both metropolitan and non-metropolitan areas.
-Additionally, the NHANES sampling design has been rigorously tested and adjusted to ensure that it accurately reflects the population in terms of demographic factors.
+The representativeness of the sample is verified through the use of these weights and by ensuring that the sample covers various geographic regions of the U.S., including both metropolitan and non-metropolitan areas [@sample].
+Additionally, the NHANES sampling design has been rigorously tested and adjusted to ensure that it accurately reflects the population in terms of demographic factors [@sample].
 
@@
 	- The NHANES dataset contains missing data, which can be categorized as either unit nonresponse or component/item nonresponse.
-Unit nonresponse occurs when an individual selected to participate in the survey does not respond during either the interview or examination phase.
-For example, during the 2009-2010 cycle, of the 13,272 individuals eligible for participation, only 10,537 completed the household interview, leading to an interview nonresponse rate of 21%.
-Furthermore, of the interviewed participants, only 10,253 participated in the Medical Examination Center (MEC) examination, contributing to an additional 2% of nonresponse during the examination phase.
-This nonresponse is addressed by applying sample weights that adjust for the nonresponse.
+Unit nonresponse occurs when an individual selected to participate in the survey does not respond during either the interview or examination phase [@analytic].
+For example, during the 2009-2010 cycle, of the 13,272 individuals eligible for participation, only 10,537 completed the household interview, leading to an interview nonresponse rate of 21% [@analytic].
+Furthermore, of the interviewed participants, only 10,253 participated in the Medical Examination Center (MEC) examination, contributing to an additional 2% of nonresponse during the examination phase [@analytic].
+This nonresponse is addressed by applying sample weights that adjust for the nonresponse [@analytic].
 Component/item nonresponse refers to missing data from specific survey components, such as not all participants opting to complete a particular health examination (e.g., a blood pressure measurement).
-Additionally, NHANES uses specific codes for missing values, such as a period (.) for numeric variables and blank spaces for character variables.
-Responses like "refused" or "don't know" are also treated as missing and are assigned specific codes (e.g., 7, 77, or 777 for "refused" and 9, 99, or 999 for "don't know").
-These should also be treate as missing data to avoid distorting analysis results.
+Additionally, NHANES uses specific codes for missing values, such as a period (.) for numeric variables and blank spaces for character variables [@analytic].
+Responses like "refused" or "don't know" are also treated as missing and are assigned specific codes (e.g., 7, 77, or 777 for "refused" and 9, 99, or 999 for "don't know") [@analytic].
+These should also be treated as missing data to avoid distorting analysis results.
 
@@
 However, given the structure and design of NHANES, there are important considerations for subsetting and combining data that influence how data is prepared for analysis.
-Since NHANES uses a complex, multi-stage sampling design, any analysis must account for the sampling weights and stratification to avoid bias.
+Since NHANES uses a complex, multi-stage sampling design, any analysis must account for the sampling weights and stratification to avoid bias [@analytic].
 
@@
 	- Age is recorded in years and categorized into decades.
-The dataset includes participants across a wide age range, with individuals aged 80 and over intentionally oversampled to ensure adequate representation of this subgroup.
+The dataset includes participants across a wide age range, with individuals aged 80 and over intentionally oversampled to ensure adequate representation of this subgroup [@sample].
 	- Race is categorized as Mexican, Hispanic, White, Black, Asian, or Other.
-Non-Hispanic Black persons and Hispanic persons are intentionally oversampled to improve the reliability and precision of estimates for these subpopulations.
-	- Income is categorized using a poverty ratio, which reflects a range of socioeconomic statuses, with specific attention given to low-income white groups.
-	- Gender is categorized as male and female, with the dataset typically having an approximately equal distribution of males and females.
+Non-Hispanic Black persons and Hispanic persons are intentionally oversampled to improve the reliability and precision of estimates for these subpopulations [@sample].
+	- Income is categorized using a poverty ratio, which reflects a range of socioeconomic statuses, with specific attention given to low-income white groups [@sample].
+	- Gender is categorized as male and female, with the dataset typically having an approximately equal distribution of males and females [@sample].
 
@@
 If so, please describe how.*
-	- No, it is not possible to identify individuals from the dataset
+	- No, it is not possible to identify individuals from the dataset.
+Data were edited such that all direct personal identifiers, as well as any characteristics that could lead to identification, were omitted from the data sets [@plan].
 
@@
 	Furthermore, the dataset includes biometric data such as weight, height, and blood test results.
-While NHANES does not include genetic data or government identification numbers (such as Social Security numbers), the presence of health and demographic variables may still pose confidentiality risks if improperly handled.
-However, strict measures are in place to protect participant privacy, including anonymization, ethical review processes, and federal confidentiality protections.
+While NHANES does not include genetic data or government identification numbers, the presence of health and demographic variables may still pose confidentiality risks if improperly handled.
+However, strict measures are in place to protect participant privacy, including anonymization, ethical review processes, and federal confidentiality protections [@plan].
 
@@
 	- The data associated with each instance in the NHANES dataset was primarily acquired through both directly observable measurements and self-reported survey responses.
-For instance, health data such as blood pressure, body mass index (BMI), and laboratory test results were directly measured during health examinations conducted at mobile examination centers (MECs).
+For instance, health data such as blood pressure, body mass index (BMI), and laboratory test results were directly measured during health examinations conducted at mobile examination centers (MECs) [@plan].
 These direct observations are objective and typically subject to standardized procedures to ensure accuracy and consistency.
 
-	In contrast, demographic and lifestyle information (e.g., age, gender, race, smoking habits, physical activity) were self-reported by participants through structured interviews.
+	In contrast, demographic and lifestyle information (e.g., age, gender, race, smoking habits, physical activity) were self-reported by participants through structured interviews [@plan].
 This data is subjective and relies on the accuracy and honesty of the respondents.
 
-	To enhance the reliability of the dataset and minimize biases, the self-reported data was verified and validated in several ways.
-First, sample weights are applied to correct for unequal probabilities of selection and nonresponse.
-For example, oversampling of certain subpopulations, like racial minorities and low-income groups, was performed, and the sample weights adjust for these oversampling techniques.
+	To enhance the reliability of the dataset and minimize biases, self-reported data were verified and validated through multiple approaches.
+First, cross-validation with objective measures was performed whenever possible [@plan].
+Standardized questionnaires, designed based on validated instruments and periodically reviewed, were administered by trained interviewers to ensure consistency in data collection [@plan].
+Built-in logic checks identified implausible or inconsistent responses during interviews, prompting clarifications or follow-up questions [@plan].
+Proxy reporting was allowed when participants, such as children, were unable to respond directly.
+
+Sample weights were applied to correct for unequal probabilities of selection and nonresponse [@plan].
+For example, oversampling of subpopulations, including racial minorities and low-income groups, was performed, and sample weights adjusted for these techniques.
+This comprehensive approach to verification and adjustment reduces bias and enhances the validity of the dataset.
 
@@
 These centers are equipped with specialized medical equipment to directly measure participants’ health metrics.
-The collection of these data points is validated by well-established clinical protocols and the use of calibrated equipment to ensure the accuracy of the measurements.
+The collection of these data points is validated by well-established clinical protocols and the use of calibrated equipment to ensure the accuracy of the measurements [@plan].
 	- Survey Interviews: Participants also answered detailed surveys that included demographic, socioeconomic, and lifestyle-related questions.
-This data was gathered through structured interviews conducted by trained personnel using electronic devices such as tablets.
-The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors.
-For instance, if a participant was unable to understand or respond in English, interpreters were made available to facilitate communication.
-The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections.
-The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors.
-The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections.
+This data was gathered through structured interviews conducted by trained personnel using electronic devices such as tablets [@plan].
+The interviewers followed strict protocols to ensure uniformity across interviews and minimize errors [@plan].
+The responses provided by participants were validated by cross-referencing answers within the survey and ensuring consistency across different sections [@plan].
 
@@
 	- Sample selection for NHANES followed 4 stages:
-	Primary Sampling Units (PSUs): In the first stage, primary sampling units, which are typically counties or groups of contiguous counties, are selected with probability proportional to size (PPS).
-This means that PSUs with larger populations have a higher probability of being selected.
-This approach helps ensure that the sample reflects the distribution of the population, with oversampling occurring for certain groups of interest, such as racial minorities, to improve the reliability of estimates for these subgroups.
+	- Primary Sampling Units (PSUs): In the first stage, primary sampling units, which are typically counties or groups of contiguous counties, are selected with probability proportional to size (PPS) [@plan].
+This means that PSUs with larger populations have a higher probability of being selected [@plan].
+This approach helps ensure that the sample reflects the distribution of the population, with oversampling occurring for certain groups of interest, such as racial minorities, to improve the reliability of estimates for these subgroups [@plan].
 
-Segmentation: After selecting the PSUs, the next stage involves dividing the selected PSUs into smaller segments, typically geographic units such as city blocks.
-These segments are then chosen using PPS to ensure an adequate representation of different population groups.
+  - Segmentation: After selecting the PSUs, the next stage involves dividing the selected PSUs into smaller segments, typically geographic units such as city blocks [@plan].
+These segments are then chosen using PPS to ensure an adequate representation of different population groups [@plan].
 
-Dwelling Units (DUs): The third stage involves selecting dwelling units (households) within the chosen segments.
-In areas with higher concentrations of specific groups, such as low-income or minority populations, these households are selected at a higher rate to ensure proper representation of these groups.
+  - Dwelling Units (DUs): The third stage involves selecting dwelling units (households) within the chosen segments [@plan].
+In areas with higher concentrations of specific groups, such as low-income or minority populations, these households are selected at a higher rate to ensure proper representation of these groups [@plan].
 
-Selection of Individuals: In the final stage, individuals are randomly selected from within the households.
-The selection is done within designated age, sex, and race/ethnicity subdomains to achieve a balance across these demographic characteristics.
-This step ensures that the sample includes a diverse range of individuals and that subgroups, such as the elderly or certain racial/ethnic populations, are adequately represented.
+  - Selection of Individuals: In the final stage, individuals are randomly selected from within the households [@plan].
+The selection is done within designated age, sex, and race/ethnicity subdomains to achieve a balance across these demographic characteristics [@plan].
+This step ensures that the sample includes a diverse range of individuals and that subgroups, such as the elderly or certain racial/ethnic populations, are adequately represented [@plan].
 
   - To ensure that specific demographic subgroups are sufficiently represented, NHANES uses oversampling techniques.
-For example, non-Hispanic black, Hispanic, and low-income white individuals, as well as those aged 80 and older, are oversampled.
+For example, non-Hispanic black, Hispanic, and low-income white individuals, as well as those aged 80 and older, are oversampled [@plan].
 This oversampling allows for more precise estimates for these groups, which may otherwise be underrepresented in a simple random sample.
 
-- Due to the complex sampling design, sample weights are applied to adjust for unequal probabilities of selection and to account for nonresponse.
+  - Due to the complex sampling design, sample weights are applied to adjust for unequal probabilities of selection and to account for nonresponse [@plan].
 These weights allow analysts to produce nationally representative estimates, as they correct for the oversampling of certain subgroups and for any nonresponse bias.
@@
 The NHANES protocol was developed and reviewed to be in compliance with the U.S.
-Department of Health and Human Services (HHS) Policy for Protection of Human Research Subjects, as outlined in 45 CFR part 46, which can be accessed at [HHS Policy for Protection of Human Research Subjects](http://www.hhs.gov/ohrp/humansubjects/guidance/45cfr46.html).
+Department of Health and Human Services (HHS) Policy for Protection of Human Research Subjects, as outlined in 45 CFR part 46, which can be accessed at [the official website of the U.S.
+Department of health and human services](http://www.hhs.gov/ohrp/humansubjects/guidance/45cfr46.html).
 
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
+  - Before being approached by NHANES staff, participants receive an advance letter.
+This letter outlines the purpose of the survey, the types of data to be collected, and reassures individuals about the confidentiality of their information.
+Example text in the letter includes details about why the participant was chosen and how their data will contribute to public health research.
 
-	![consent form](/Users/hxw/marriage/other/datasheet/consent.png)
+	![advance](advanceletter.png)
 
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- yes, and it is shown in the consent form provided.
+	- Before any data collection begins, participants are required to sign a written informed consent form.
+These forms clearly state that participation is voluntary, it provide assurances about privacy and confidentiality, highlighting that data will be used only for research purposes, and offer participants the opportunity to ask questions and withdraw at any point without any repercussions.
+		![consent form](consent.png)
 
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- yes, and this information is shown at [participant FAQ](https://www.cdc.gov/nchs/nhanes/participant/participant-faq.htm).
+	- yes, NHANES emphasizes that participation is entirely voluntary.
+Participants are explicitly told that they can refuse to participate in any part of the survey or withdraw from the study entirely at any point during the data collection process without facing any negative consequences.
+This information is shown at [participant FAQ](https://www.cdc.gov/nchs/nhanes/participant/participant-faq.htm).
 
@@
 If not, you may skip the remaining questions in this section.*
-	- NHANES uses specific codes for "refused" and "don't know" responses, assigning values such as 7, 77, or 777 for refusals, and 9, 99, or 999 for "don't know" responses.
+	- NHANES uses specific codes for "refused" and "don't know" responses, assigning values such as 7, 77, or 777 for refusals, and 9, 99, or 999 for "don't know" responses [@analytic].
 
@@
 Researchers have used NHANES data to analyze the prevalence of different health conditions, identify risk factors, evaluate the impact of lifestyle choices (such as diet, physical activity, and smoking) on health outcomes, and inform public health policies.
+
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- Some of the product can be found [here](https://www.cdc.gov/nchs/nhanes/nhanes_products.htm).
+	- Some of the products can be found [here](https://www.cdc.gov/nchs/nhanes/nhanes_products.htm).
 
@@
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- The data can be downloaded directly from the NHANES page on the CDC official website
+	- The data can be downloaded directly from the NHANES page on the CDC official website.
 
 3. *When will the dataset be distributed?*
-	- The NHANES 2009-2010 data were made available after the data collection period ended
+	- The NHANES 2009-2010 data were made available after the data collection period ended.
 
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
+  - The NHANES dataset is provided under strict confidentiality protections, and data use is limited to statistical analysis.
+There are severe legal penalties for violating the confidentiality and data use conditions.
+Users must agree to these terms before using the dataset, ensuring compliance with the applicable laws and ethical guidelines.
 	- Data Use Agreement can be found at [this website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- DLicensing terms and fees associated with restriction can be found at [the website](https://www.cdc.gov/nchs/policy/data-user-agreement.html)
+	- No
 
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- No
+	- There are no export controls or regulatory restrictions like those typically imposed on military or sensitive commercial data.
+The NHANES dataset is governed by federal confidentiality laws, and users are required to adhere to data use restrictions as outlined in the Data Use Agreement.
 
@@
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- You can contact NHANES staff by calling 1 (800) 232-4636
+	- You can contact NHANES staff by calling 1 (800) 232-4636.
 

### 2024-12-15 other/datasheet/datasheet_template.qmd
update paper, scripts, and llm

@@
 ---
-title: "Datasheet for NHANES dataset'"
+title: "Datasheet for 'NHANES dataset'"
 author: 

### 2024-12-15 paper/paper.qmd
update paper, scripts, and llm

@@
 library(broom)
+library(kableExtra)
 ```
@@
 Given its importance, understanding the factors that influence BMI, such as socioeconomic and lifestyle variables, has become an essential area of public health research.
-This paper aims to address the relationship about how variables like poverty, physical activity, age, sleep duration, and gender interact to influence BMI outcomes.
+This paper aims to address the relationship about how variables like poverty, physical activity, sleep duration, age and gender interact to influence BMI outcomes.
 
-Using data from the US National Health and Nutrition Examination Survey (NHANES), this study models log-transformed BMI as a function of five predictors: poverty level, physical activity frequency (measured in days), age, sleep duration, and gender.
-A multilinear regression approach was employed to quantify these relationships and identify patterns within the dataset.
+Using resampled version of the data from the US National Health and Nutrition Examination Survey (NHANES), this study models log-transformed BMI as a function of five predictors: poverty level, physical activity frequency (measured in days), age, sleep duration, and gender.
+A multiple linear regression approach was employed to quantify these relationships and identify patterns within the dataset.
+The estimand in this study is the expected change in log-transformed BMI resulting from a one-unit change in each predictor variable, holding all other variables constant.
 
-The results indicate that while the correlations between BMI and these predictors are generally weak, several significant relationships are observed.
+The results indicate that while the correlations between log(BMI) and these predictors are generally weak, several significant relationships are observed.
 Poverty is associated with a 0.01 decrease in log(BMI), suggesting that higher income corresponds to lower BMI levels.
@@
 
-The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows.
+@sec-data provides an overview and measurement of the dataset, as well as an introduction to the variables.
+@sec-model presents the model setup and justification.
+@sec-result discusses the results of the model.
+@sec-discussion provides a detailed discussion of the results.
+@sec-data-details offers a more in-depth justification of the data and discusses the surveys and sampling methods.
+Finally, @sec-model-details examines the diagnostics of the model by analyzing the assumptions of linear regression.
 
@@
 
-The dataset used in this analysis is derived from the US National Health and Nutrition Examination Survey (NHANES), version 2.1.0.
+The dataset used in this analysis is derived from the 2009-2010 cycle of the US National Health and Nutrition Examination Survey (NHANES).
 This version of the dataset includes survey results collected between October 2009 and December 2010.
@@
 Since 1999, approximately 5,000 individuals from various age groups have been interviewed annually in their homes and undergone health examinations at mobile examination centers (MEC).
+
 Two datasets in this package were considered for this analysis: NHANESraw, which is the original raw data, and NHANES, a resampled version of the NHANES data.
@@
 NHANES is used in this analysis due to its ability to reduce the potential biases from the complex survey design in NHANESraw.
-Additional details about this choice are provided in Appendix A.
+Additional details about this choice are provided in @sec-data-justication.
 The data used here was originally compiled by Michelle Dalrymple from Cashmere High School and Chris Wild from the University of Auckland for educational purposes.
@@
 Specifically, variables such as BMI, poverty index, physical activity days, sleep hours, gender, and age were retained.
-After cleaning the missing values in the dataset, 3,573 observations remained.
+After cleaning the missing values and the duplicate rows in the dataset, 2841 observations remained.
 
-The dataset was prepared, cleaned, and analyzed using R [@citeR] with the following libraries: tidyverse [@tidyverse] and dplyr [@dplyr] for data manipulation, ggplot2 [@ggplot2] and patchwork [@patchwork] for visualizations, and broom [@broom] for model summaries.
+The dataset was prepared, cleaned, and analyzed using R [@citeR] with the following libraries: tidyverse [@tidyverse] and dplyr [@dplyr] for data manipulation, ggplot2 [@ggplot2], kableExtra [@kableExtra] and patchwork [@patchwork] for visualizations, and broom [@broom] for model summaries.
 The arrow [@arrow] library was used for efficient data storage and retrieval, while knitr [@knitr] facilitated report generation.
@@
 
-A summary table of cleaned data is shown in table 1.
+A summary table of cleaned data is shown in @tbl-summary.
 
@@
 #| echo: false
-#| label: table-summary
-#| tbl-cap: "Summary statistics for variables in the NHANES dataset."
+#| label: tbl-summary
+#| tbl-cap: "Summary statistics for `BMI`, `log(BMI)`, `Poverty Index`, `Physical Activity Days`, `Sleep Hours`, `Age`, and `Gender`."
 
 # Load the data
-nhanes_data <- read_parquet("/Users/hxw/marriage/data/02-analysis_data/clean_data.parquet")
+nhanes_data <- read_parquet("../data/02-analysis_data/clean_data.parquet")
+
+# Calculate the counts of males and females
+gender_counts <- nhanes_data %>%
+  count(Gender) %>%
+  pivot_wider(names_from = Gender, values_from = n, values_fill = 0)
+
+# Extract the number of females and males
+num_females <- gender_counts$female[1]  
+num_males <- gender_counts$male[1]
 
@@
       "Physical Activity Days",
+      "Sleep Hours", 
       "Age",
-      "Sleep Hours"
+      "Gender"
     ),
@@
       mean(Age),
-      mean(SleepHrsNight)
+      mean(SleepHrsNight),
+      NA
     ), 3),
@@
       median(Age),
-      median(SleepHrsNight)
+      median(SleepHrsNight),
+      NA
     ), 3),
-    Min = round(c(
-      min(BMI),
-      min(log(BMI)),
-      min(Poverty),
-      min(PhysActiveDays),
-      min(Age),
-      min(SleepHrsNight)
-    ), 3),
-    Max = round(c(
-      max(BMI),
-      max(log(BMI)),
-      max(Poverty),
-      max(PhysActiveDays),
-      max(Age),
-      max(SleepHrsNight)
-    ), 3),
+    Min = c(
+      round(min(BMI), 3),
+      round(min(log(BMI)), 3),
+      round(min(Poverty), 3),
+      round(min(PhysActiveDays), 3),
+      round(min(Age), 3),
+      round(min(SleepHrsNight), 3),
+      paste(num_females, "(females)")
+    ),
+    Max = c(
+      round(max(BMI), 3),
+      round(max(log(BMI), 3)),
+      round(max(Poverty), 3),
+      round(max(PhysActiveDays), 3),
+      round(max(Age), 3),
+      round(max(SleepHrsNight), 3),
+      paste(num_males, "(males)")
+    ),
     `1st Quantile` = round(
@@
         quantile(Age, 0.25),
-        quantile(SleepHrsNight, 0.25)
+        quantile(SleepHrsNight, 0.25),
+        NA
       ),
@@
         quantile(Age, 0.75),
-        quantile(SleepHrsNight, 0.75)
+        quantile(SleepHrsNight, 0.75),
+        NA
       ),
@@
 
-# Create the summary table using kable
+# Render the table without styling
 summary_table %>%
-  kable()
+  kable(
+    format = "html",
+    col.names = c(
+      "Variable", "Mean", "Median", "Min", "Max", 
+      "1st Quantile", "3rd Quantile"
+    )
+  )
 ```
@@
 #| message: false
-#| label: fig-bmi-logbmi
+#| label: fig-bmi
 #| fig-cap: "Distributions of BMI and log(BMI) in the NHANES dataset."
+#| fig-subcap: ["Distribution of BMI", "Distribution of log(BMI)"]
 #| echo: false
-#| fig.width: 8
-#| fig.height: 4
+#| layout-ncol: 2
+#| fig.width: 4
+#| fig.height: 6
 
@@
                  color = "black") +
-  labs(title = "BMI Distribution", x = "BMI", y = "Frequency") +
+  labs(x = "BMI", y = "Frequency") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 14),
-    axis.title = element_text(size = 12),
-    axis.text = element_text(size = 10)
-  )
+  theme(axis.title = element_text(size = 12),
+        axis.text = element_text(size = 12))
 
@@
                  color = "black") +
-  labs(title = "log(BMI) Distribution", x = "log(BMI)", y = "Frequency") +
+  labs(x = "log(BMI)", y = "Frequency") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 14),
-    axis.title = element_text(size = 12),
-    axis.text = element_text(size = 10)
-  )
+  theme(axis.title = element_text(size = 12),
+        axis.text = element_text(size = 10))
 
-# Figure 1: BMI and log(BMI)
-figure_bmi <- (hist_bmi | hist_log_bmi)
-figure_bmi
+hist_bmi
+hist_log_bmi
 
@@
 #| fig-cap: "Distributions of predictor variables in the NHANES dataset, including Poverty, Physical Activity Days, Age, Sleep Hours, and Gender."
+#| fig-subcap: ["Distribution of Poverty Index", "Physical Activity Days Distribution", "Age Distribution", "Sleep Hours Distribution", "Gender Distribution"]
 #| echo: false
+#| layout-ncol: 3
 #| fig.width: 8
@@
   ) +
-  labs(title = "Poverty Index Distribution", x = "Poverty Index", y = "Frequency") +
+  labs(x = "Poverty Index", y = "Frequency") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 14),
-    axis.title = element_text(size = 12),
-    axis.text = element_text(size = 10)
-  )
+  theme(axis.title = element_text(size = 24),
+        axis.text = element_text(size = 18))
 
@@
   ) +
-  labs(title = "Physical Activity Days Distribution", x = "Physical Activity Days", y = "Frequency") +
+  labs(x = "Physical Activity Days", y = "Frequency") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 8)
-  )
+  theme(axis.title = element_text(size = 24),
+        axis.text = element_text(size = 18))
 
@@
   ) +
-  labs(title = "Age Distribution", x = "Age", y = "Frequency") +
+  labs(x = "Age", y = "Frequency") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 8)
-  )
+  theme(axis.title = element_text(size = 24),
+        axis.text = element_text(size = 18))
 
@@
                  color = "black") +
-  labs(title = "Sleep Hours Distribution", x = "Sleep Hours", y = "Frequency") +
+  labs(x = "Sleep Hours", y = "Frequency") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 8)
-  )
+  theme(axis.title = element_text(size = 24),
+        axis.text = element_text(size = 18))
 
@@
   geom_bar(fill = "lightgray", color = "black") +
-  labs(title = "Gender Distribution", x = "Gender", y = "Count") +
+  labs(x = "Gender", y = "Count") +
   theme_minimal() +
-  theme(
-    plot.title = element_text(size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 8)
-  )
+  theme(axis.title = element_text(size = 24),
+        axis.text = element_text(size = 18))
 
-# Figure 2: Predictor Variables
-figure_predictors <- (hist_poverty | hist_physactive | hist_age) /
-  (hist_sleep | hist_gender) +
-  plot_annotation(caption = "Figure 2: Distributions of predictor variables in the NHANES dataset, including Poverty, Physical Activity Days, Age, Sleep Hours, and Gender.",
-                  theme = theme(plot.caption = element_text(hjust = 0.5, size = 12)))
-figure_predictors
+hist_poverty
+hist_physactive
+hist_age
+hist_sleep
+hist_gender
 
@@
 
-The NHANES dataset aims to provide a comprehensive view of the health and nutritional status of the U.S.
+The NHANES dataset provides a comprehensive view of the health and nutritional status of the U.S.
 population, transforming real-world phenomena into structured data entries.
@@
 population using a complex, multistage probability sampling design.
-This ensures that the sample is representative of the civilian, non-institutionalized population, while also oversampling certain subgroups, such as racial minorities, to ensure sufficient data for subgroup analysis.
+This ensures that the sample is representative of the civilian, non-institutionalized population, while also oversampling certain subgroups, such as racial minorities, to ensure sufficient data for subgroup analysis [@sample].
 Once selected, individuals are surveyed on various health and lifestyle factors, such as their eating habits, physical activity, medical conditions, and demographics.
@@
 The process of measurement involves both self-reported data and direct observations.
-For example, data on an individual’s lifestyle habits, such as hours of physical activity, alcohol consumption, or smoking, is obtained through self-reports in interviews.
+For example, data on an individual’s lifestyle habits, such as hours of physical activity, alcohol consumption, or smoking, is obtained through self-reports in interviews [@plan].
 These responses are recorded as variables in the dataset, and any missing values or refusals are appropriately coded.
-On the other hand, physical measurements like height, weight, blood pressure, and cholesterol levels are directly taken in the MEC using medical equipment.
+On the other hand, physical measurements like height, weight, blood pressure, and cholesterol levels are directly taken in the MEC using medical equipment [@plan].
 These physical measurements are then processed and entered into the dataset.
@@
 Missing values may arise if a participant refuses to answer a particular question or does not undergo a specific examination.
-These missing values are systematically handled by assigning special codes such as a period (.) for numeric variables or blanks for character variables, ensuring that they are not treated as valid data.
+These missing values are systematically handled by assigning special codes such as a period (.) for numeric variables or blanks for character variables, ensuring that they are not treated as valid data [@analytic].
 Furthermore, to mitigate potential bias due to missing data, adjustments are made using sample weights to produce national estimates that are representative of the U.S.
@@
 
-In the case of variables related to health measurements, the data undergo further validation through the use of sampling weights and variance estimation to ensure that the final dataset accurately reflects the population’s health status.
+In the case of variables related to health measurements, the data undergo further validation through the use of sampling weights and variance estimation to ensure that the final dataset accurately reflects the population’s health status [@sample].
 This process involves using the complex survey design parameters, such as the primary sampling unit (PSU) and strata, to adjust the data accordingly, so that analyses can account for oversampling of certain subpopulations and non-response during data collection.
-Thus, every entry in the dataset is an outcome of rigorous data collection methods, reflecting a specific health measure or lifestyle factor that has been transformed into a quantifiable variable, which can then be analyzed and used for public health research.
+
+For this analysis, a resampled version of the NHANES dataset, referred to as NHANES, was used.
+NHANES includes 10,000 resampled observations, and it is derived from the original NHANESraw dataset, which contains 20,293 observations.
+The resampling process helps reduce biases associated with the complex survey design in the raw dataset, particularly biases arising from oversampling specific subpopulations.
+This simplified dataset eliminates the effects of oversampling and allows for more straightforward analysis.
+
+The resampled NHANES dataset is structured to reflect a simplified, but still representative, version of the U.S.
+population, addressing potential sampling imbalances that might arise in the raw data due to overrepresentation of certain groups [@nhanes].
+It is particularly important in this analysis because it minimizes biases related to the complex survey design, making it more suitable for modeling relationships between different factors and log(BMI).
+By resampling and adjusting for the complex survey design parameters, NHANES ensures that the relationships observed between variables are more accurate and generalizable to the larger population.
+
+Thus, every entry in the NHANES dataset is an outcome of rigorous data collection methods, reflecting a specific health measure or lifestyle factor transformed into a quantifiable variable.
+These variables have been adjusted to account for complex survey design effects and missing data, ensuring the dataset used in the analysis is robust, representative, and suitable for informing public health research.
 
@@
 BMI is widely used to assess healthy weight relative to height, and its relevance to health outcomes such as cardiovascular disease and diabetes has been well-established.
-For this analysis, BMI was log-transformed to address its skewed distribution shown in Figure 1, providing a better fit for statistical modeling.
+For this analysis, BMI was log-transformed to address its skewed distribution shown in @fig-bmi, providing a better fit for statistical modeling.
 
 ## Predictor variables
-The following predictor variables were examined to assess the potential lifestyle and socio-economic factors influencing BMI:
+The following predictor variables were examined to assess the potential lifestyle and socio-economic factors influencing log(BMI) across different gender and age groups:
 
@@
 This variable is recorded for individuals aged 12 years and older.
-- `Sleep Duration (SleepHrsNight)`: The self-reported average number of hours of sleep a participant receives on weekdays or workdays.
-This variable is recorded for individuals aged 16 years and older.
+- `Sleep Hour (SleepHrsNight)`: The self-reported average number of hours of sleep a participant receives on weekdays or workdays. This variable is recorded for individuals aged 16 years and older.
 - `Gender`: The gender of the participant, categorized as male or female.
@@
 ### Distribution of Predictor Variables
-The summary statistics presented in Figure 1 and the histograms of predictor variables shown in Figure 3 provide insights into the distribution of these variables:
+The summary statistics presented in @tbl-summary and the histograms of predictor variables shown in @fig-predictor-distributions provide insights into the distribution of these variables:
 
@@
 - `Physical Activity Days (PhysActiveDays)`: The number of days participants engage in physical activity ranges from 2 to 7, with a mean value of 3.7 days per week.
-- `Sleep Duration (SleepHrsNight)`:The number of hours participants sleep each night ranges from 2 to 12 hours, with a mean of 6.96 hours.
-The distribution of this variable approximates a normal curve.
+- `Sleep Hour (SleepHrsNight)`:The number of hours participants sleep each night ranges from 2 to 12 hours, with a mean of 6.96 hours. The distribution of this variable approximates a normal curve.
 - `Gender`: The gender distribution is nearly balanced, with 1,814 male participants and 1,759 female participants.
@@
 
-# Model
+# Model {#sec-model}
 
@@
 ### Model justification
-We use a multiple linear regression model to estimate the relationship between body mass index (BMI) and various predictors, including poverty index, physical activity days, age, sleep hours, and gender.
+We use a multiple linear regression model to estimate the relationship between body mass index (BMI) and various predictors, including poverty index, physical activity days, sleep hours, and gender.
 The model is designed to predict log-transformed BMI, as this transformation helps normalize the distribution of BMI and address skewness.
@@
 
-# Results
+# Results {#sec-result}
 
@@
 # Load the saved linear model
-lm_model <- readRDS("/Users/hxw/marriage/models/lm_model.rds")
+lm_model <- readRDS("../models/lm_model.rds")
 # Tidy the model summary
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## What is done in this paper? {#sec-first-point}
+## What is done in this paper?
 
@@
 
-# Appendix {-}
+# Appendix {{#sec-append}}
 
@@
 
-## Data Justication
+## Data Justication {#sec-data-justication}
 The NHANES_raw dataset provides a comprehensive collection of data from the American National Health and Nutrition Examination Surveys (NHANES), including 20,293 observations spanning 75 variables.

### 2024-12-15 scripts/00-simulate_data.R

@@ -1,16 +1,17 @@
 #### Preamble ####
-# Purpose: Simulates the dataset
+# Purpose: Simulates the cleaned NHANES dataset
 # Author: Sakura Hu
 # Date: 01 December 2024
 # Contact: Sakura.Hu@utoronto.ca
 # License: MIT
-# Pre-requisites: The `dplyr` package must be installed
+# Pre-requisites: The `dplyr` and `arrow` package must be installed
 # Any other information needed? Make sure you are in the `bmi` rproj
 
 
 
 #### Workspace setup ####
 library(dplyr)
+library(arrow)
 set.seed(1009201917)
 
 
@@ -22,15 +23,15 @@ n <- 100  # Number of observations
 simulated_data <- data.frame(
   BMI = rnorm(n, mean = 15, sd = 6),
   Poverty = sample(0:5, n, replace = TRUE),
-  PhysActiveDays = sample(1:7, n, replace = TRUE),
   # Simulating physical activity days (1-7 scale)
-  Age = sample(16:80, n, replace = TRUE),
+  PhysActiveDays = sample(1:7, n, replace = TRUE),
   # Simulating ages (16 to 80 years)
-  SleepHrsNight = sample(2:12, n, replace = TRUE),
+  Age = sample(16:80, n, replace = TRUE),
   # Simulating hours of sleep (4-12 hours)
+  SleepHrsNight = sample(2:12, n, replace = TRUE),
   Gender = sample(c("male", "female"), n, replace = TRUE)  # Simulating gender
 )
 
 
 #### Save data ####
-write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")
+write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")

### 2024-12-15 scripts/01-test_simulated_data.R

@@ -5,7 +5,7 @@
 # Contact: Sakura.Hu@utoronto.ca
 # License: MIT
 # Pre-requisites:
-# - The `tidyverse`, `testthat`, and `pointblank` package must be installed and loaded
+# - The `tidyverse`, `testthat`, `arrow` and `pointblank` package must be installed and loaded
 # - 00-simulate_data.R must have been run
 # Any other information needed? Make sure you are in the `bmi` rproj
 
@@ -14,11 +14,12 @@
 library(testthat)
 library(pointblank)
 library(tidyverse)
+library(arrow)
 
 
 
 #### Test data ####
-simulated_data <- read_csv("/Users/hxw/marriage/data/00-simulated_data/simulated_data.csv")
+simulated_data <- read_parquet("../data/00-simulated_data/simulated_data.parquet")
 
 
 
@@ -59,7 +60,7 @@ test_that("PhysActiveDays values should be between 1 and 7", {
   ))
 })
 
-# 8. Test for Outliers in 'SleepHrsNight' using testthat
+# 7. Test for Outliers in 'SleepHrsNight' using testthat
 test_that("SleepHrsNight values should be between 2 and 12", {
   expect_true(all(
     simulated_data$SleepHrsNight >= 2 &
@@ -67,18 +68,18 @@ test_that("SleepHrsNight values should be between 2 and 12", {
   ))
 })
 
-# 9. Check the Distribution of Gender using testthat
+# 8. Check the Distribution of Gender using testthat
 test_that("Gender should only be male or female", {
   expect_true(all(simulated_data$Gender %in% c("male", "female")))
 })
 
-# 10. Check for Data Type Consistency using testthat
+# 9. Check for Data Type Consistency using testthat
 test_that("Data types should match expectations", {
   expect_is(simulated_data$BMI, "numeric")
-  expect_is(simulated_data$Poverty, "numeric")
-  expect_is(simulated_data$PhysActiveDays, "numeric")
-  expect_is(simulated_data$Age, "numeric")
-  expect_is(simulated_data$SleepHrsNight, "numeric")
+  expect_is(simulated_data$Poverty, "integer")
+  expect_is(simulated_data$PhysActiveDays, "integer")
+  expect_is(simulated_data$Age, "integer")
+  expect_is(simulated_data$SleepHrsNight, "integer")
   expect_is(simulated_data$Gender, "character")
 })
 

### 2024-12-15 scripts/02-download_data.R

@@ -22,3 +22,4 @@ data("NHANES")
 write_parquet(NHANES, "data/01-raw_data/raw_data.parquet")
 
          
+

### 2024-12-15 scripts/03-clean_data.R

@@ -4,7 +4,7 @@
 # Date: 01 December 2024
 # Contact: sakura.hu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 # - The raw marriage data must be downloaded and saved as a parquet to data/raw_data.
 # - The `tidyverse` packages must be installed and loaded.
 # - 02-download_data.R must have been run.
@@ -22,14 +22,10 @@ raw_data <- read_parquet("data/01-raw_data/raw_data.parquet")
 clean_data <- raw_data %>%
   select(BMI, Poverty, PhysActiveDays, Age, SleepHrsNight, Gender) %>%
   filter(
-    !is.na(BMI),
-    !is.na(Poverty),
-    !is.na(PhysActiveDays),
-    !is.na(Age),
-    !is.na(SleepHrsNight),
-    !is.na(Gender)
+    !is.na(BMI),!is.na(Poverty),!is.na(PhysActiveDays),!is.na(Age),!is.na(SleepHrsNight),!is.na(Gender)
   ) %>%
   distinct()  # Remove duplicate rows
+
 
 #### Save data ####
 write_parquet(clean_data, "data/02-analysis_data/clean_data.parquet")

### 2024-12-15 scripts/04-test_analysis_data.R

@@ -18,7 +18,7 @@ library(arrow)
 
 
 #### Test data ####
-analysis_data <- read_parquet("/Users/hxw/marriage/data/02-analysis_data/clean_data.parquet")
+analysis_data <- read_parquet("../data/02-analysis_data/clean_data.parquet")
 
 
 
@@ -59,7 +59,7 @@ test_that("PhysActiveDays values should be between 1 and 7", {
   ))
 })
 
-# 8. Test for Outliers in 'SleepHrsNight' using testthat
+# 7. Test for Outliers in 'SleepHrsNight' using testthat
 test_that("SleepHrsNight values should be between 2 and 12", {
   expect_true(all(
     analysis_data$SleepHrsNight >= 2 &
@@ -67,12 +67,12 @@ test_that("SleepHrsNight values should be between 2 and 12", {
   ))
 })
 
-# 9. Check the Distribution of Gender using testthat
+# 8. Check the Distribution of Gender using testthat
 test_that("Gender should only be male or female", {
   expect_true(all(analysis_data$Gender %in% c("male", "female")))
 })
 
-# 10. Check for Data Type Consistency using testthat
+# 9. Check for Data Type Consistency using testthat
 test_that("Data types should match expectations", {
   expect_is(analysis_data$BMI, "numeric")
   expect_is(analysis_data$Poverty, "numeric")

### 2024-12-15 scripts/06-model_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models the marriage rate
+# Purpose: Model log(BMI) as a function of Poverty, PhysActiveDays, SleepHrsNight, Gender and Age
 # Author: Sakura Hu
 # Date: 01 December 2024
 # Contact: sakura.hu@mail.utoronto.ca

### 2024-12-15 paper/paper.qmd
wrapping up

@@
 
-The goal of our modelling strategy is to use multilinear regression model to investigate the relationship between log(BMI) and poverty, Physical Activity Days, Sleep Duration, gender and age. 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The goal of this analysis is to use a multiple linear regression model to investigate the relationship between the log-transformed Body Mass Index (log(BMI)) and several predictors: poverty level, physical activity days, sleep duration, gender, and age.
+These variables were selected based on their known or hypothesized influence on BMI, as supported by prior research and health literature.
+The log-transformation of BMI is applied to address skewness in the data and to better approximate a normal distribution, which is an assumption for linear regression models.
+
+Further background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $log(BMI)_i$ as the log(BMI).
-Then $\beta_i$ are the coefficients associated with each predictor variable, which represent the change in $log(BMI)_i$ for a one-unit change in the corresponding predictor, while holding all other predictors constant.
+Let $log(BMI)_i$ represent the log-transformed BMI for the $i$-th individual. The multiple linear regression model is defined as:
 
-\begin{equation*} 
-\log(\text{BMI}_i) = \beta_0 + \beta_1 \cdot \text{Poverty}_i + \beta_2 \cdot \text{PhysActiveDays}_i + \beta_3 \cdot \text{Age}_i + \beta_4 \cdot \text{SleepHrsNight}_i + \beta_5 \cdot \text{Gender}_i + \epsilon_i
-\end{equation*}
-\begin{equation*}
-\epsilon_i \sim \text{Normal}(0, \sigma^2)
-\end{equation*}
+\begin{equation*} \log(\text{BMI}_i) = \beta_0 + \beta_1 \cdot \text{Poverty}_i + \beta_2 \cdot \text{PhysActiveDays}_i + \beta_3 \cdot \text{Age}_i + \beta_4 \cdot \text{SleepHrsNight}_i + \beta_5 \cdot \text{Gender}_i + \epsilon_i \end{equation*}
 
-We ran the model in R [@citeR] using the lm() function for linear regression, with data manipulation performed using the dplyr package and data reading via the arrow package.
-No specific priors were applied, as this model relies on ordinary least squares (OLS) estimation, which assumes no prior distributions for the coefficients.
+where:
+
+- $log(BMI)_i$ is the log-transformed body mass index for the $i$-th individual,
+- $\beta_0$ is the intercept, representing the baseline log(BMI) when all predictors are zero,
+- $\beta_1$ through $\beta_5$ are the coefficients associated with each predictor, representing the change in $log(BMI)_i$ for a one-unit increase in the corresponding predictor, while holding all other predictors constant,
+- $\epsilon_i$ is the error term, assumed to follow a normal distribution: $\epsilon_i \sim \text{Normal}(0, \sigma^2)$.
+
+This model was fitted using the lm() function in R [@citeR], with data manipulation performed using the dplyr package and data storage managed by the arrow package.
+As this is an ordinary least squares (OLS) regression model, no specific priors were applied, and the coefficients were estimated directly from the data.
 
 ### Model justification
-We use a multiple linear regression model to estimate the relationship between body mass index (BMI) and various predictors, including poverty index, physical activity days, sleep hours, and gender.
-The model is designed to predict log-transformed BMI, as this transformation helps normalize the distribution of BMI and address skewness.
-This approach allows us to explore how these lifestyle and socio-economic factors influence BMI across the sample, using high-quality survey data from the NHANES dataset.
-We employ predictors like poverty, physical activity, age, sleep hours, and gender to account for key factors that are known to influence BMI, based on existing research.
+We chose a multiple linear regression model because it is well-suited for estimating the relationship between a continuous dependent variable (log-transformed BMI) and multiple independent variables, including both numerical and categorical predictors (e.g., physical activity days, age, poverty, sleep hours, and gender).
+This method is interpretable and provides straightforward estimates of the effect of each predictor on BMI.
 
-We use linear regression because it is appropriate for modeling the relationship between a continuous outcome variable (log(BMI)) and predictors physical activity, sleep hours, age, poverty, and gender.
-This method is straightforward to interpret, and the results could quantify the effect of predictors on BMI, making it a suitable choice for analyzing how these factors relate to BMI.
+The decision to log-transform BMI was driven by the variable’s right-skewed distribution.
+Log-transforming BMI improves the normality of its distribution, which is an important assumption for linear regression.
+It also helps stabilize the variance across levels of BMI, reducing the potential for heteroscedasticity, and enables a more linear relationship between BMI and the predictors.
 
-We chose to log-transform the BMI variable due to its right-skewed distribution.
-Log-transforming BMI allows us to better meet the assumptions of linear regression by stabilizing variance and making the relationship between BMI and predictors more linear.
-This is particularly important for ensuring that the model’s estimates are valid and interpretable.
+`Poverty` was included as a predictor to account for socio-economic status, as prior studies [@webber2023bmi] have shown that lower income is often associated with higher BMI.
+`PhysActiveDays` captures the number of days an individual engages in physical activity each week, with increased physical activity generally linked to a healthier BMI [@webber2023bmi].
+`Age` is included because BMI naturally changes with age, with older individuals often having higher BMI values due to changes in metabolism and lifestyle.
+`SleepHrsNight` reflects the amount of sleep an individual gets, as insufficient sleep is known to contribute to weight gain and higher BMI [@ekstedt2013sleep].
+Lastly, `Gender` is included because research consistently finds gender differences in BMI, with men generally having lower BMI than women [@longosilva2023sleep].
+The choice to treat gender as a categorical variable is justified because gender is a nominal variable with distinct, non-ordinal categories.
+For this analysis, gender was encoded as a binary variable (male, female), which allows us to estimate the effect of gender on BMI.
 
-We included the variable 'Poverty' to account for socio-economic status, as previous research has suggested that lower-income individuals tend to have higher BMI levels (Webber et al., 2023).
-'PhysActiveDays' was included to capture the effect of physical activity on BMI, as increased physical activity is typically associated with a lower BMI(Webber et al., 2023).
-Age was included as a predictor to account for the natural changes in BMI that occur as individuals age.
-Sleep hours were added because there is evidence that insufficient sleep can contribute to weight gain (Ekstedt et al., 2013).
-Gender was included as a predictor due to well-established gender differences in BMI, with males typically having lower BMI than females (Longo-Silva et al., 2023).
+The model is based on the assumption that the relationship between the predictors and log(BMI) is linear, and that the errors are normally distributed with constant variance (homoscedasticity).
+While linear regression provides a reliable and interpretable method for analyzing the relationship between BMI and the chosen predictors, it does not account for potential interactions between variables.
+This model assumes that the effect of each predictor is independent of the others, which may not fully capture the complexities of the relationships between the predictors and BMI.
 
-We used the default settings in lm() from the stats package, which assumes normally distributed errors and does not apply any specific prior distributions, as this method does not require priors in the same way that Bayesian methods do.
-This approach provides a reliable way to assess the linear relationship between the predictors and BMI.
-However, we acknowledge that other methods, such as Bayesian regression or generalized linear models, could be used for more complex modeling, but this approach was selected for its simplicity and interpretability given the goals of the analysis.
+Some other models that were considered were models including interaction terms, such as between poverty and physical activity.
+However, when these interaction terms were added, the model’s fit decreased (as evidenced by a lower R-squared value) and the residual plot indicated potential model misspecification.
+Given these results, we decided to exclude interaction terms to avoid overfitting and maintain a more parsimonious model.
+Future analyses with larger datasets could revisit this approach, potentially including interactions or testing alternative modeling techniques to capture more complex relationships.
 
-Initially, we considered including interaction terms between predictors (such as between poverty and physical activity).
-However, when these interaction terms were added, the R-squared value decreased, indicating a reduced fit to the data.
-Additionally, the residual plot showed a noticeable concentration in the residuals, suggesting potential model misspecification or overfitting.
-As a result, we decided to exclude interaction terms to maintain a more interpretable and well-fitted model.
-Future analyses could revisit this approach with a larger dataset or alternative modeling strategies to better account for potential interactions.
-
-By using this model, we aim to better understand the factors that influence BMI and provide insights into potential public health interventions that could target lifestyle changes and socio-economic factors to reduce BMI and related health risks.
+The model was implemented using R, and all results were validated through diagnostic checks.
+Specifically, we examined the residual plots to assess the assumptions of linearity, normality of errors, and homoscedasticity.
+Additional validation techniques, including out-of-sample testing, could be incorporated in future iterations to further assess the model's predictive performance.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in @tbl-modelresults, and the correlations between predictos and log(BMI) are plotted in @fig-predictor-bmi.
+The findings indicate that the selected factors collectively have a minimal influence on BMI, as evidenced by the low R-squared value (0.0246), This differs from the conclusions of prior studies such as @ekstedt2013sleep and @longosilva2023sleep, which reported stronger effects, likely due to the inclusion of interaction terms that are not part of this analysis.
+Nevertheless, individual predictors still show significant associations with log(BMI), as indicated by p-values below 0.05 for all predictors except `PhysActiveDays` are lower than 0.05 shows that these predictos are significant.
+For example, being male increases the average log(BMI) by 0.0172, which is consistent with the findings of @ekstedt2013sleep.
+Poverty is negatively associated with BMI, where a one-unit increase in the poverty index is associated with a decrease of 0.0109 in the average log(BMI).
+This result contradicts the findings of @webber2023bmi, which reported a positive relationship between poverty and BMI.
+The discrepancy may stem from differences in data sources, as this analysis uses NHANES data from the 2009–2010 cycle, whereas @webber2023bmi examined data from 2017 onwards.
+We also observed a positive relationship between age and BMI, with the average log(BMI) increasing by 0.0014 for each one-unit increase in age.
+Additionally, our findings confirm that increased sleep duration and physical activity are associated with lower BMI.
+Specifically, each additional day of physical activity in a week decreases the average log(BMI) by 0.0035, while each additional hour of sleep per night reduces the average log(BMI) by 0.0108.
+These observations align with the conclusions of @ekstedt2013sleep and @longosilva2023sleep, supporting the hypothesis that healthier lifestyles contribute to lower BMI levels.
 
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Summary statistics for variables in the NHANES dataset."
+#| tbl-cap: "This table presents the estimated coefficients, standard errors, test statistics, and p-values for the predictors included in the multiple linear regression model analyzing the relationship between log-transformed BMI and poverty level, physical activity days, sleep duration, gender, and age.
+The R-squared value indicates the proportion of variance in log-transformed BMI explained by the model."
 
@@
 model_summary_with_r2 %>%
-  kable(caption = "Summary of the Linear Model for Log(BMI)")
+  kable()
 ```
@@
 #| label: fig-predictor-bmi
-#| fig-cap: "Scatter plots of predictors vs. log(BMI) with fitted regression lines."
-#| fig-subcap: ["Age vs. log(BMI)","Gender vs. log(BMI)", "Poverty vs. log(BMI)", "SleepHrsNight vs. log(BMI)","Physical Active Days vs. log(BMI)"]
+#| fig-cap: "This figure presents the relationships between log-transformed BMI and the predictors in the model.
+`Panel a` shows the possitive relationship between age and log(BMI).
+`Panel b` compares the distribution of log(BMI) across genders.
+`Panel c` illustrates the negative correlation between poverty level and log(BMI), while `Panel d` depicts the negative relationship between sleep duration (in hours) and log(BMI).
+Finally, `Panel e` shows the negative correlation between the number of physically active days per week and log(BMI)"
+#| fig-subcap: ["Age vs. log(BMI)","Gender vs. log(BMI)", "Poverty vs. log(BMI)", "Sleep Duration vs. log(BMI)","Physical Active Days vs. log(BMI)"]
 #| layout-ncol: 3
@@
   theme_minimal() +
-  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+  theme(axis.title = element_text(size = 20), axis.text = element_text(size = 20))
 
@@
 
-page This paper explores the relationship between Body Mass Index (BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
+This paper explores the relationship between Body Mass Index (BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
 The analysis is performed using a linear regression model, which allows us to estimate how each of these predictors influences BMI, as measured by its log-transformed values.

### 2024-12-15 scripts/00-simulate_data.R

@@ -10,28 +10,25 @@
 
 
 #### Workspace setup ####
-library(dplyr)
-library(arrow)
-set.seed(1009201917)
-
+# Load necessary libraries
+library(dplyr)  # for data manipulation
+library(arrow)  # for reading and writing Parquet files
+set.seed(1009201917)  # Set the random seed for reproducibility of results
 
 #### Simulate data ####
 # Simulating data for the predictors
-n <- 100  # Number of observations
+n <- 100  # Define the number of observations (100 rows of data)
 
-# Simulating values based on the provided data
+# Simulating values for different predictors based on the specified parameters
 simulated_data <- data.frame(
-  BMI = rnorm(n, mean = 15, sd = 6),
-  Poverty = sample(0:5, n, replace = TRUE),
-  # Simulating physical activity days (1-7 scale)
-  PhysActiveDays = sample(1:7, n, replace = TRUE),
-  # Simulating ages (16 to 80 years)
-  Age = sample(16:80, n, replace = TRUE),
-  # Simulating hours of sleep (4-12 hours)
-  SleepHrsNight = sample(2:12, n, replace = TRUE),
-  Gender = sample(c("male", "female"), n, replace = TRUE)  # Simulating gender
+  BMI = rnorm(n, mean = 15, sd = 6),  # Simulating BMI values with a normal distribution (mean = 15, sd = 6)
+  Poverty = sample(0:5, n, replace = TRUE),  # Simulating Poverty level as integer values between 0 and 5
+  PhysActiveDays = sample(1:7, n, replace = TRUE),  # Simulating physical activity days (1 to 7 days a week)
+  Age = sample(16:80, n, replace = TRUE),  # Simulating Age as integer values between 16 and 80
+  SleepHrsNight = sample(2:12, n, replace = TRUE),  # Simulating hours of sleep (between 2 to 12 hours)
+  Gender = sample(c("male", "female"), n, replace = TRUE)  # Simulating gender with equal probability of male or female
 )
 
-
 #### Save data ####
-write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")
+# Save the simulated data to a Parquet file for efficient storage
+write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")  # Write the dataframe to a Parquet file

### 2024-12-15 paper/paper.qmd
update paper and llmusage

@@
 
-This paper explores the relationship between Body Mass Index (BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
+This paper explores the relationship between log(BMI) and several key lifestyle and demographic factors, including poverty, physical activity, age, sleep duration, and gender.
 The analysis is performed using a linear regression model, which allows us to estimate how each of these predictors influences BMI, as measured by its log-transformed values.
@@
 
-The model used in this study, a linear regression model, is a fundamental yet powerful tool that helps to identify the strength and direction of the relationships between predictors and BMI.
+The model used in this study, a multiple linear regression model, is a fundamental yet powerful tool that helps to identify the strength and direction of the relationships between predictors and BMI.
 The results provide a valuable starting point for understanding how changes in lifestyle and demographic factors may affect BMI.
-However, while the model is useful, it is not without its limitations.
+However, while the model is useful, it has its limitations.
 For instance, it assumes that the relationships between the predictors and BMI are linear, which may not always be the case.
@@
 The negative coefficient for the poverty variable suggests that individuals in poverty tend to have higher BMI, on average, than those with higher income levels.
-This result is consistent with a growing body of literature that links lower socioeconomic status to obesity and poor health outcomes.
 It may seem counterintuitive at first—since poverty is often associated with limited access to healthy foods and exercise—but the correlation can be explained by several factors.
@@
 
+Another avenue for improvement involves the application of model selection criteria, such as Akaike Information Criterion (AIC) or Bayesian Information Criterion (BIC), to systematically compare different model specifications.
+By testing multiple models with varying combinations of predictors and interaction terms, AIC or BIC could help identify a model that balances explanatory power with parsimony.
+This approach would allow for the identification of additional variables or interactions that may influence log(BMI) while avoiding overfitting.
+Incorporating model selection techniques could also provide a clearer understanding of which variables contribute meaningfully to BMI variation, guiding the development of a more robust and interpretable model.
+
 Moving forward, there are several steps that could be taken to address these weaknesses.
@@
 Second, using a non-linear model or exploring transformations of the predictors might better capture the relationships between BMI and the explanatory variables.
-Finally, addressing the possibility of interaction effects and testing different model specifications could enhance the robustness of the results.
+Third, addressing the possibility of interaction effects and testing different model specifications could enhance the robustness of the results.
 This could include experimenting with non-parametric models, such as random forests or gradient boosting machines, to better handle the complexities of the data.
+Finally, employing model selection criteria like AIC or BIC during the exploratory phase would ensure that the final model is both parsimonious and comprehensive.
 By expanding the scope of the analysis and refining the model, future work could yield more precise estimates and offer more actionable insights for public health interventions.
@@
 
-# Appendix {{#sec-append}}
+# Appendix {#sec-append}
 
@@
 ## Data Justication {#sec-data-justication}
-The NHANES_raw dataset provides a comprehensive collection of data from the American National Health and Nutrition Examination Surveys (NHANES), including 20,293 observations spanning 75 variables.
-This dataset includes additional variables that describe the sample weighting scheme employed to account for the complex survey design.
-However, despite its breadth and richness, NHANES_raw introduces complexities in analysis due to the oversampling of certain subpopulations, such as racial minorities.
-This sampling approach necessitates the use of survey weights and other design-specific parameters to obtain unbiased estimates and valid statistical inferences.
+The NHANES_raw dataset represents a rich and expansive collection of data from the American National Health and Nutrition Examination Surveys (NHANES).
+It encompasses 20,293 observations across 75 variables, including data on health, nutrition, and demographic factors.
+Additionally, NHANES_raw incorporates variables describing the sample weighting scheme employed to account for its complex, multistage survey design.
+This design includes oversampling of certain subpopulations, such as racial and ethnic minorities, to improve the precision of estimates for these groups.
+While this approach enhances its utility for population-level research, it introduces complexities for analysis, particularly for researchers unfamiliar with survey design methodologies.
 
-Naïve analysis of NHANES_raw—without accounting for the sample design and weights—can lead to significant biases and erroneous conclusions.
-For instance, the racial composition in NHANES_raw does not represent the true demographic distribution of the U.S.
-population due to oversampling adjustments.
-As a result, researchers must account for these weights in any analysis to avoid overstating significance levels and generating inaccurate results.
-This makes NHANES_raw unsuitable for straightforward analysis in contexts where the primary goal is to demonstrate simple statistical relationships, especially for educational purposes.
+A critical limitation of NHANES_raw is its reliance on survey weights to account for the oversampling of subpopulations and ensure representativeness of the U.S.
+population.
+Naïve analyses that disregard these weights can yield misleading results.
+For example, the raw racial composition in NHANES_raw does not reflect the true demographic distribution of the U.S.
+population due to intentional oversampling adjustments.
+Failure to account for the survey weights risks overstating statistical significance, generating biased estimates, and drawing inaccurate conclusions.
+As such, analyses based on NHANES_raw require expertise in survey statistics and careful implementation of weighting techniques to produce valid results.
 
-In contrast, the NHANES dataset, which is a resampled subset of NHANES_raw, addresses the complexities associated with the oversampling design.
-With 10,000 observations and the same 75 variables, NHANES is simplified to approximate a simple random sample from the U.S.
+For the purposes of this study, the NHANES dataset, a simplified resampled subset of NHANES_raw, was selected.
+This subset comprises 10,000 observations and retains the same 75 variables but approximates a simple random sample from the U.S.
 population.
-This resampling process removes the need for researchers to manually account for the oversampling effects, enabling analyses that are easier to interpret and less prone to methodological errors for educational purposes.
+The resampling process mitigates the challenges associated with the original survey design by removing the need to manually account for oversampling effects and survey weights.
+This simplification makes NHANES particularly suitable for educational applications, as it allows for straightforward statistical analyses without requiring advanced knowledge of survey methodologies.
+Furthermore, the subset retains sufficient variability to explore meaningful relationships between variables while reducing the risk of misinterpretation arising from unaddressed biases in the original dataset.
 
-The decision to use NHANES in this paper was driven by its appropriateness for demonstrating relationships between body mass index (BMI) and lifestyle, poverty, age, and gender.
-NHANES allows for clear and reliable analyses without requiring specialized expertise in survey design or sampling weights, making it ideal for this study’s educational focus.
-The dataset enables meaningful exploration of public health questions while minimizing the risk of misinterpretation due to unaddressed biases in the sampling framework.
+The decision to use NHANES in this paper was guided by its alignment with the study's educational focus and analytical goals.
+Specifically, it provides a clean and interpretable framework for investigating the relationships between body mass index (BMI) and factors such as lifestyle, poverty, age, and gender.
+By simplifying the sampling complexities of the original dataset, NHANES ensures that the analyses presented in this paper are accessible to a broader audience, including those less familiar with survey weighting procedures.
 
-It is important to acknowledge that NHANES is adapted for educational purposes and is not intended for formal research.
-Researchers conducting advanced studies should rely on the original NHANES_raw data and adhere to the prescribed sampling and weighting procedures to ensure the validity of their findings.
-Future research could extend the current analysis by using NHANES_raw in combination with survey weighting techniques to explore population-level health trends and disparities with greater accuracy.
+It is important to recognize that while NHANES is tailored for educational purposes, it is not suitable for formal research aimed at generating population-level inferences.
+Researchers conducting such studies should rely on NHANES_raw and adhere strictly to the prescribed sampling and weighting procedures to maintain the validity and accuracy of their findings.
+Future extensions of this analysis could utilize NHANES_raw in conjunction with survey weighting techniques to examine population-level health trends and disparities with greater precision.
+Additionally, incorporating variables specific to the survey design—such as strata and cluster identifiers—could enable a more comprehensive exploration of the complexities underlying the relationships between health outcomes and sociodemographic factors.
+This approach would provide a more robust framework for addressing nuanced public health questions at the national level.
 
 # Surveys, Sampling, and Observational Data {#sec-sampling-details}
-The National Health and Nutrition Examination Survey (NHANES) represents one of the most comprehensive and influential health datasets in the United States, providing a valuable resource for understanding the health and nutritional status of the U.S.
+
+## Methodology Analysis
+### Introduction
+
+The National Health and Nutrition Examination Survey (NHANES) is a critical tool for understanding the health and nutritional status of the U.S.
 population.
-Conducted by the National Center for Health Statistics (NCHS), NHANES gathers both interview and physical examination data, which are combined to produce estimates of the general population’s health, nutritional status, and related behaviors.
-The methodology behind the NHANES survey is complex and carefully designed to ensure that the data collected are representative of the U.S.
-civilian, non-institutionalized population.
+Managed by the National Center for Health Statistics (NCHS), NHANES gathers comprehensive data through interviews and physical examinations, providing invaluable insights into the health behaviors and chronic conditions affecting diverse groups.
+This essay aims to explore NHANES’s methodology in-depth, including its target population, sampling strategy, recruitment process, non-response handling, and data collection techniques.
 
-The target population of NHANES consists of the civilian, non-institutionalized population of the United States, including individuals of all ages.
-This broad and inclusive definition ensures that the data captured by NHANES reflect the health and nutritional status of nearly every demographic group in the country.
-However, as a complex survey design, NHANES also uses a stratified, multistage sampling approach to select participants, ensuring that certain subgroups, particularly those with greater health disparities, are adequately represented.
-To achieve this goal, NHANES selects a representative sample from all counties in the U.S.
-Each year, a new group of PSUs (Primary Sampling Units) is chosen, which typically consist of counties or groups of contiguous counties.
-A total of about 12,000 people participate in each two-year cycle.
-This sampling method incorporates differential probabilities of selection, ensuring that groups at higher risk of health issues or underrepresentation (e.g., racial minorities, elderly individuals) are more likely to be sampled.
-As a result, NHANES oversamples certain subgroups, such as non-Hispanic Black individuals, Hispanic individuals, and elderly individuals over the age of 80, to improve the precision and reliability of health estimates for these populations.
+### Target Population and Sampling Methodology
 
-The recruitment process for NHANES is critical to ensuring that the sample is representative and that response rates are maximized.
-The process begins by selecting households through a multi-stage sampling design.
-In the first stage, PSUs are chosen using probability proportional to size (PPS), ensuring that more populous areas are selected with higher likelihood.
-In the second stage, segments within the PSUs are selected—typically representing census blocks or other local geographic units.
-In the third stage, households within the segments are listed, and a sample of households is chosen.
-Finally, individuals are selected within these households, using a method that ensures the representation of key demographic characteristics such as age, sex, and race/ethnicity.
-On average, two participants are chosen per eligible household, which allows the survey to gather a substantial amount of data on family structures, as well as individual health outcomes.
+NHANES aims to represent the civilian, non-institutionalized U.S.
+population, encompassing individuals of all ages, genders, and racial/ethnic groups.
+The survey’s sampling strategy is designed to be representative of the entire U.S.
+population and includes specific oversampling of groups that are underrepresented or have health disparities.
+This methodology allows researchers to obtain reliable estimates of health outcomes across different demographic groups.
 
-The sampling approach used by NHANES is probabilistic, which means that each person in the target population has a known, non-zero probability of being selected.
-This is in contrast to deterministic approaches, which might introduce bias by excluding certain groups or individuals from the sample.
-By employing a probabilistic method, NHANES ensures that its data can be generalized to the entire U.S.
-population, although care must be taken when analyzing smaller subgroups, given the smaller sample sizes in these categories.
-One of the trade-offs of this probabilistic sampling approach is the increased complexity of the survey design.
-Given the multi-stage sampling procedure, survey weights and variance estimation methods must be carefully applied during the data analysis phase to adjust for the unequal probabilities of selection and the clustering of respondents within geographic regions.
-These adjustments are necessary to avoid biased estimates, particularly when estimating health indicators for subgroups or when combining data across multiple survey cycles.
+#### Stratified, Multistage Sampling
 
-Non-response is a common challenge in large-scale surveys like NHANES, and its handling is critical to ensuring that the data remain unbiased and representative.
-Non-response in NHANES can occur at both the unit (or sample person) level and the component (or item) level.
-Unit non-response refers to individuals who are selected to participate in the survey but either refuse to participate or fail to respond to any part of the survey (e.g., household interview or medical examination).
-In the 2009-2010 cycle, for example, of the 13,272 persons eligible to participate, 21% failed to complete the household interview, and a further 2% of those who completed the interview did not participate in the medical examination.
-These non-responses were adjusted for using sampling weights, which are designed to reflect the number of individuals in the population represented by each sample respondent.
+NHANES employs a **stratified, multistage sampling design** to select participants, ensuring diverse representation and reducing sampling bias.
+The process begins with the selection of Primary Sampling Units (PSUs), which are typically counties or groups of contiguous counties.
+These PSUs are chosen using a probability proportional to size (PPS) method, ensuring that more populous areas have a higher likelihood of being selected.
 
-Component non-response, on the other hand, refers to missing data for specific questions or tests within the survey.
-For example, a respondent may refuse to have their blood pressure measured but complete all other examination components.
-NHANES addresses component non-response by treating missing values as missing and adjusting the weights accordingly.
-When analyzing the data, researchers are encouraged to evaluate the extent of missing data for their variables of interest and to apply reweighting or imputation techniques if necessary, particularly when more than 10% of the data for a given variable is missing.
-While NHANES employs rigorous methods to handle non-response, it remains a potential source of bias.
-Non-respondents may differ in key characteristics from respondents, such as age, gender, or health status.
-This is particularly true for elderly individuals or those with more severe health issues, who may be less likely to participate in the survey.
-Therefore, the results of NHANES should always be interpreted with caution, especially when analyzing specific subgroups or when drawing conclusions about less-represented populations.
+The sampling process proceeds through several stages:
+1. **PSU Selection**: Using PPS, counties or groups of counties are selected.
+2. **Segment Selection**: Segments, often representing census blocks, are chosen within selected PSUs.
+3. **Household Selection**: Households within selected segments are identified and sampled.
+4. **Individual Selection**: Individuals are selected within households, ensuring balanced representation across demographics such as age, gender, and race.
 
-The NHANES questionnaire and data collection process are designed to capture a comprehensive range of health, nutritional, and demographic information.
-The questionnaire consists of multiple sections, including detailed questions on demographic characteristics (e.g., age, sex, race, income), health behaviors (e.g., smoking, alcohol consumption, physical activity), and medical history (e.g., chronic diseases, medication use).
-The questionnaire also covers dietary intake, which is crucial for understanding the population’s nutritional status.
+This **probabilistic design** allows each person in the target population to have a known, non-zero probability of selection, making it a powerful tool for generalizing the results to the U.S.
+population.
 
-The questionnaire is administered during a household interview, which is followed by a physical examination at the Mobile Examination Centers (MEC).
-During the MEC visit, participants undergo a range of tests, including anthropometric measurements (e.g., height, weight, BMI), blood pressure measurements, and laboratory tests (e.g., blood, urine samples).
-The tests performed in the MEC allow for objective measurements of participants’ health, complementing the self-reported information collected during the interview.
+#### Oversampling and Stratification
 
-The NHANES questionnaire is continuously updated to reflect new public health concerns and emerging health trends.
-For example, over time, the survey has included questions related to emerging issues such as mental health, sleep patterns, and environmental exposures.
-However, the questionnaire also has limitations.
-For example, self-reported data on health behaviors like physical activity or dietary intake may be subject to recall bias, with participants underestimating or overestimating their behaviors.
-Additionally, some participants may be reluctant to report sensitive information, such as smoking or alcohol consumption, which can further skew the data.
+One of the key strengths of NHANES’s sampling design is its **oversampling of certain subgroups**.
+Specifically, NHANES oversamples non-Hispanic Black individuals, Hispanic individuals, and elderly individuals, especially those over the age of 80.
+This approach ensures that the survey yields sufficiently accurate and reliable estimates for these populations, which may otherwise be underrepresented in a simple random sample.
 
-One of the major strengths of the NHANES methodology is its ability to provide nationally representative estimates of health and nutritional status across a wide range of demographic and geographic subgroups.
-By combining interviews with objective physical examinations and laboratory tests, NHANES offers a rich, multi-dimensional view of health in the U.S.
+This stratified sampling approach ensures that key demographic groups are adequately represented, which is particularly important when assessing health disparities in the U.S. population.
+
+#### Variance Estimation and Survey Weights
+
+Given the multi-stage, stratified design, NHANES data require careful handling during analysis.
+**Survey weights** are applied to adjust for unequal probabilities of selection.
+These weights correct for the fact that individuals in more populous areas have a higher chance of selection, and they help adjust for the over- or underrepresentation of certain subgroups.
+
+Additionally, the sampling clusters within PSUs introduce **intra-cluster correlation**, meaning that individuals within the same PSU are more likely to share similar characteristics than individuals across PSUs.
+Variance estimation methods, such as Taylor Series Linearization or Balanced Repeated Replication, are used to account for this correlation in order to generate accurate confidence intervals and significance tests.
+
+### Recruitment Process
+
+The recruitment process for NHANES is designed to maximize participation rates while ensuring the sample remains representative of the U.S.
 population.
-The rigorous sampling and data collection procedures ensure that the data can be used for a wide variety of public health analyses, from assessing chronic disease prevalence to tracking health trends over time.
+Each stage in the sampling process is carefully designed to engage diverse populations, reduce bias, and address barriers to participation.
 
-However, NHANES also has several weaknesses.
-The most notable is the issue of non-response, particularly in certain subgroups (e.g., elderly individuals, people with poor health).
-While the survey adjusts for non-response using weights, there is always the possibility that the non-respondents differ systematically from the respondents, which could lead to biased estimates.
-Additionally, the reliance on self-reported data can introduce biases such as social desirability bias or recall bias, which can affect the accuracy of responses on health behaviors and lifestyle factors.
+#### Stage 1: PSU Selection
+Primary Sampling Units (PSUs), typically counties or groups of contiguous counties, are selected using PPS.
+This ensures that larger counties with higher populations have a higher probability of being selected.
 
-Moreover, the fact that NHANES data are released in two-year cycles means that estimates for some subgroups may not be stable, particularly for rare health conditions or smaller demographic groups.
-Combining data across multiple years can help mitigate this issue, but it also introduces complexities in terms of data harmonization and analytic guidelines.
+#### Stage 2: Segment and Household Selection
+Within each PSU, geographic segments are selected, often representing census blocks. From these segments, households are selected, ensuring a mix of rural, suburban, and urban areas.
 
-In conclusion, NHANES provides a valuable and unique resource for understanding the health and nutritional status of the U.S.
+#### Stage 3: Individual Selection
+Within each household, individuals are chosen to participate in the survey, with selection methods that account for key demographic variables such as age, gender, and ethnicity.
+By choosing individuals based on these criteria, NHANES ensures that the sample is balanced across relevant characteristics.
+
+### Non-Response and Data Adjustments
+
+Non-response is a common issue in large-scale surveys, and NHANES employs multiple strategies to minimize its impact on the results.
+Non-response can occur at two levels: unit non-response (refusals to participate) and item non-response (failure to respond to specific questions).
+
+#### Unit Non-Response
+Unit non-response occurs when selected individuals refuse to participate or are unable to participate for other reasons.
+In the 2009-2010 cycle, for instance, 21% of eligible participants did not complete the household interview, and 2% of those who completed the interview refused the medical examination.
+Non-response at the unit level is adjusted by applying **sampling weights** that reflect the demographic characteristics of non-respondents.
+
+#### Item Non-Response
+Item non-response happens when respondents skip or refuse to answer specific questions or tests, such as blood pressure measurements or questions about smoking habits.
+NHANES addresses item non-response through the use of imputation techniques or by applying weights that account for missing data.
+
+### Data Collection and Questionnaire Design
+
+NHANES collects an extensive range of health and nutrition data through interviews and physical examinations, providing a rich dataset for public health research.
+The survey includes a variety of sections, such as:
+
+1. **Demographic Information**: Age, sex, race, income, education level.
+2. **Health Behaviors**: Smoking, alcohol consumption, physical activity levels.
+3. **Medical History**: Chronic diseases, medication use, and past health diagnoses.
+4. **Dietary Intake**: Detailed dietary recalls, including information about calorie and nutrient intake.
+
+#### Physical Examinations
+Participants undergo a series of medical tests at Mobile Examination Centers (MECs), which include:
+- **Anthropometric Measurements**: Height, weight, and BMI.
+- **Blood Pressure**: Both systolic and diastolic blood pressure measurements.
+- **Laboratory Tests**: Blood and urine samples to assess biochemical markers of health.
+
+These objective measurements complement the self-reported data from the interviews, providing a more complete picture of participants' health status.
+
+#### Limitations of Self-Reported Data
+While NHANES includes objective measurements, it also relies heavily on **self-reported data**, which can be prone to biases such as recall bias or social desirability bias.
+For instance, respondents may underreport behaviors like alcohol consumption or smoking, or overestimate their physical activity levels.
+This introduces potential inaccuracies, especially for health behaviors that are sensitive or socially stigmatized.
+
+### Strengths and Limitations of NHANES
+
+#### Strengths
+NHANES provides robust, nationally representative data that can be used to track health trends, monitor disease prevalence, and guide public health policy.
+The **multi-dimensional data collection**—which includes both subjective interviews and objective examinations—offers a comprehensive understanding of health issues across the U.S.
 population.
-Its robust sampling methodology, comprehensive questionnaire, and use of both self-reported and objective health measures make it an indispensable tool for public health research.
-While the survey has several strengths, including its representativeness and ability to assess health trends over time, it also faces challenges related to non-response, data quality, and biases inherent in self-reported information.
-Researchers must be mindful of these issues when analyzing NHANES data, and apply appropriate statistical methods to account for potential biases.
-Nonetheless, NHANES remains a cornerstone of U.S.
-public health surveillance, providing critical insights into the health and well-being of the nation’s diverse population.
+
+Additionally, the **oversampling of subgroups** ensures that groups typically underrepresented in national surveys are adequately studied, which enhances the generalizability of findings to diverse populations.
+
+#### Limitations
+Despite its strengths, NHANES faces several limitations:
+1. **Non-response**: Even with the application of weights, non-response can introduce bias, especially among older adults or individuals in poor health.
+2. **Self-Report Bias**: The reliance on self-reported data for behaviors such as diet, physical activity, and substance use is subject to significant recall and social desirability biases.
+3.
+**Data Cycles**: NHANES data is collected in two-year cycles, which can make it challenging to estimate trends for smaller subgroups or rare health conditions.
+Combining data from multiple cycles may be necessary, but this introduces additional complexities in analysis.
+
+### Conclusion
+
+NHANES is a powerful and invaluable resource for public health research, offering detailed, nationally representative data on a wide range of health and nutritional topics.
+The survey’s complex, stratified, multistage sampling design ensures that the data are reflective of the U.S.
+population.
+Although challenges such as non-response and the limitations of self-reported data exist, NHANES remains a critical tool for understanding public health issues and guiding policy decisions.
+Researchers must apply appropriate statistical techniques to address these challenges, ensuring the robustness and accuracy of their findings.
+
+## Idealized survey
+
+The survey will be structured as follows:
+
+### Introductory Section
+
+The survey will begin with a clear introduction outlining the purpose of the survey, ensuring participants understand the goals of the study.
+This section will also describe the confidentiality measures, emphasizing that personal information will not be shared.
+Contact details for questions or concerns will be provided.
+
+### Demographics and Personal Information (Section 1)
+
+This section will collect basic information, such as age, gender, ethnicity, and socio-economic status, which are known to impact BMI.
+
+### Health and Lifestyle Factors (Section 2)
+
+This section will inquire about physical activity levels, dietary habits, alcohol consumption, smoking, and sleep patterns.
+It will include validated scales such as the International Physical Activity Questionnaire (IPAQ) and a food frequency questionnaire (FFQ).
+
+### Genetic and Family History (Section 3)
+
+Participants will be asked if they have any family history of obesity, diabetes, or cardiovascular disease, which can help identify genetic predispositions.
+
+### Psychological and Social Factors (Section 4)
+
+This section will include questions on mental health, stress levels, and social support, as these factors can also affect BMI.
+
+### BMI Measurement (Section 5)
+
+Participants will be asked to self-report their weight and height, and their BMI will be calculated.
+This will be followed by a prompt for participants to either confirm their BMI or opt to take part in a physical measurement of weight and height.
+
+### Closing Section
+
+A thank-you message will be included, and respondents will be reminded that their participation is voluntary and can be withdrawn at any time.
+
+## 3. Sampling Approach
+
+A stratified random sampling approach will be used to ensure that the survey sample is representative of the general population. The stratification will be based on key demographic factors, such as:
+
+- **Age**: Different age groups will be targeted to examine how BMI and its predictors vary across the lifespan.
+- **Gender**: Both men and women will be surveyed to investigate gender differences in BMI-related factors.
+- **Socio-economic Status**: Income and education levels will be used to examine how socio-economic factors influence BMI.
+- **Geographic Location**: Participants will be sampled from urban, suburban, and rural areas to capture regional variations in BMI and health behaviors.
+
+The sample size will be approximately 10,000 respondents, ensuring statistical power for the analysis.
+The sampling frame will be drawn from public voter registration lists, with additional recruitment through social media and community outreach to reach diverse populations.
+
+## 4. Recruitment Strategy
+
+Recruitment will be conducted through multiple channels:
+
+- **Online Surveys**: A link to the survey will be distributed via social media platforms, targeting a broad audience.
+A paid advertisement campaign will be used to ensure a diverse and representative sample.
+
+- **Community Outreach**: Partnerships with community organizations will allow for in-person recruitment, especially for populations that may be underrepresented in online surveys.
+
+- **Incentives**: Participants will receive a small financial incentive (e.g., $5) to encourage participation.
+
+## 5. Non-Response Handling
+
+To handle non-response bias, several strategies will be employed:
+
+- **Follow-up Invitations**: Non-respondents will receive two email reminders and a phone call if their contact information is available.
+- **Incentive Adjustment**: A larger incentive (e.g., $10) will be offered for participants who complete the survey within a certain time frame.
+
+## 6. Data Validation
+
+Data quality will be ensured through the following measures:
+
+- **Data Consistency Checks**: Automatic consistency checks will be built into the survey platform to flag implausible responses (e.g., extreme self-reported height or weight).
+- **Randomized Validation Sample**: A subset of respondents will be asked to visit a local clinic for physical measurements of height and weight, allowing for validation of self-reported data.
+
+## 7. Survey Questions
+
+The questions will be constructed to minimize biases and ensure reliability. The following are examples of question types:
+
+- **Demographic Questions:**
+  - "What is your age?"
+  - "What is your gender?"
+
+- **Physical Activity Questions:**
+  - "On average, how many days per week do you engage in at least 30 minutes of moderate physical activity?"
+  - "How many hours of sedentary activity (e.g., watching TV, using a computer) do you engage in per day?"
+
+- **Dietary Habits:**
+  - "How often do you consume fruits and vegetables on a typical day?"
+  - "How many servings of sugary drinks do you consume per week?"
+
+- **Psychological Factors:**
+  - "On a scale from 1 to 10, how would you rate your current stress level?"
+  - "Do you feel supported by your family and friends?"
+
+## 8. Aggregation and Statistical Methods
+
+The collected data will be aggregated and analyzed using multiple regression techniques to identify significant predictors of BMI. The following methods will be employed:
+
+- **Descriptive Statistics** will be used to summarize demographic data and BMI-related variables.
+- **Regression Analysis** will help identify key predictors of BMI (e.g., physical activity, diet, genetics).
+- **Interaction Terms** will be included to examine how combinations of factors (e.g., physical activity and diet) jointly affect BMI.
+
+## 9. Questionnaire Design and Order
+
+The survey will be structured to minimize response bias.
+Sensitive questions (e.g., those about weight and diet) will be placed at the end of the survey, once rapport has been built.
+Demographic questions will appear first to quickly categorize participants without triggering discomfort.
+
+## 10. Survey Platform
+
+The survey will be implemented using a robust platform like Google Forms or Qualtrics, allowing for automated data collection and validation.
 
@@
 Lastly, the response variable versus fitted values plot shows that observed values align with predicted values, suggesting that the model accurately predicts the response variable.
-Although the residual plots indicate that all regression assumptions are met, the predictor versus response plots show weak correlations between predictor variables and log(BMI
+Although the residual plots indicate that all regression assumptions are met, the predictor versus response plots show weak correlations between predictor variables and log(BMI).
 
@@
 #| label: fig-model-diagnostics
-#| fig-cap: "Diagnostic and Predictor Relationships in the Linear Model for log(BMI)."
+#| fig-cap: "Diagnostic plots assessing the assumptions and performance of the linear regression model for predicting log(BMI).
+The plots evaluate the residuals and fitted values to ensure the validity of the linear model.
+(1) Residuals vs.
+Fitted Values tests the assumption of homoscedasticity.
+(2) Standardized Residuals vs.
+Fitted Values examines the presence of outliers and systematic patterns.
+(3) Distribution of Standardized Residuals evaluates the normality of residuals.
+(4) Residuals vs.
+Poverty Index and (5) Residuals vs.
+Age assess the independence of residuals concerning key predictors.
+(6) Residuals vs.
+Gender compares residuals across categorical groups.
+(7) Fitted Values vs.
+Observed log(BMI) visualizes model accuracy, and (8) Q-Q Plot assesses the normality of residuals against theoretical quantiles.
+Together, these plots ensure the appropriateness of the model and identify potential violations of its assumptions."
 #| fig-subcap: ["Fitted vs Residuals", "Fitted vs Standardized Residuals", "Histogram of Standardized Residuals", "Poverty vs Residuals", "Age vs Residuals", "Gender vs Residuals", "Fitted vs log(BMI)", "Normal Q-Q Plot"]
-#| layout-ncol: 4
-#| fig.width: 12
-#| fig.height: 18
+#| layout-ncol: 3
+#| fig.width: 15
+#| fig.height: 15
 
@@
   theme_minimal() +
-  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 8))
+  theme(axis.title = element_text(size = 30), axis.text = element_text(size = 30))
 
